---
title: "Beacon EDA for Africa"
author: "Saurabh Khanna"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 4
---

```{r setup, include=FALSE}
# knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

## Summary (ongoing)

+ All
- Total OJS v2 journals found in Africa: 255
- Total OJS v2 installations found in Africa: 38
+ Active
- Total *active* OJS v2 journals found in Africa: 140
- Total *active* OJS v2 installations found in Africa: 27 

Total *active* journals worldwide (2017-19): 12178


```{r message=FALSE, warning=FALSE}
# Libraries
pacman::p_load(tidyverse, countrycode, sf, DT, htmltools, htmlwidgets, jsonlite, rgeolocate, urltools, lubridate, janitor, plotly)

# Data
df <- read_csv(here::here("data", "beacon.csv"))
shapefile <- read_sf(here::here("data/TM_WORLD_BORDERS_SIMPL-0.3.shp"))
df_pred2 <- read_csv(here::here("data", "predatory_msperlin.csv"))
tld <- read_csv(here::here("data", "tld-country.csv"))
tld_from_ip <- read_csv(here::here("data", "tld_from_ip.csv"))
df_act2019 <- read_csv(here::here("data/active", "beacon-2019.csv")) %>% select(oai_url, version, repository_name, issn, country, set_spec)
df_act2018 <- read_csv(here::here("data/active", "beacon-2018.csv")) %>% select(oai_url, version, repository_name, issn, country, set_spec)
df_act2017 <- read_csv(here::here("data/active", "beacon-2017.csv")) %>% select(oai_url, version, repository_name, issn, country, set_spec)
df_act <-
  bind_rows(
    df_act2017, df_act2018, df_act2019,
    .id = "year"
  ) %>% 
  mutate(
    year = as.integer(year) + 2016L
  ) %>% 
  arrange(desc(year), oai_url, version, repository_name, issn, country, set_spec) %>% 
  distinct(oai_url, version, repository_name, issn, country, set_spec, .keep_all = T)

rm(df_act2017, df_act2018, df_act2019)
```


```{r}
# correcting some oai urls
df <- df %>% mutate(oai_url = if_else(str_detect(oai_url, "^//"), str_c("http:", oai_url), oai_url))
df_act <- df_act %>% mutate(oai_url = if_else(str_detect(oai_url, "^//"), str_c("http:", oai_url), oai_url))
```


```{r}
df <- 
  bind_cols(
    df,
    df %>% pull(oai_url) %>% domain() %>% tld_extract()
  ) %>% 
  left_join(tld_from_ip, by = "domain") %>%
  mutate(
    tld = if_else(!is.na(tld_from_ip), tld_from_ip, tld)
  ) %>%
  left_join(tld, by = "tld")

df_act <- 
  bind_cols(
    df_act,
    df_act %>% pull(oai_url) %>% domain() %>% tld_extract()
  ) %>% 
  left_join(tld_from_ip, by = "domain") %>%
  mutate(
    tld = if_else(!is.na(tld_from_ip), tld_from_ip, tld)
  ) %>%
  left_join(tld, by = "tld")
```


```{r}
### Mapping countries to continents
df <-
  df %>% 
  mutate(
    country = if_else(is.na(country), country_clean, country),
    ojs_v2 = str_detect(version, "^ojs2/2"),
    ojs_v3 = str_detect(version, "^ojs2/3"),
    version_clean = case_when(
      ojs_v2 ~ "Version 2",
      ojs_v3 ~ "Version 3",
      TRUE ~ "Other"
    )
  )

continents <-
  df %>% 
  pull(country) %>% 
  countrycode(origin = "country.name", destination = "continent")

df <- 
  df %>%
  bind_cols(continents) %>% 
  rename(continent = `...20`)

df_act <-
  df_act %>% 
  mutate(
    country = if_else(is.na(country), country_clean, country),
    ojs_v2 = str_detect(version, "^ojs2/2"),
    ojs_v3 = str_detect(version, "^ojs2/3"),
    version_clean = case_when(
      ojs_v2 ~ "Version 2",
      ojs_v3 ~ "Version 3",
      TRUE ~ "Other"
    )
  )

continents <-
  df_act %>% 
  pull(country) %>% 
  countrycode(origin = "country.name", destination = "continent")

df_act <- 
  df_act %>%
  bind_cols(continents) %>% 
  rename(continent = `...15`)
```


```{r, eval = F}
df %>% summarize_at(vars(contains("country")), ~ sum(is.na(.)))
df_act %>% summarize_at(vars(contains("country")), ~ sum(is.na(.)))
```

```{r}
# merging morocco and western sahara
shapefile <-
  shapefile %>% 
  janitor::clean_names() %>% 
  mutate(
    name = if_else(name == "Western Sahara", "Morocco", name)
  ) %>%
  arrange(name) %>% 
  group_by(name) %>% 
  summarize(
    geometry = st_union(geometry),
    lat = first(lat),
    lon = first(lon),
    region = first(region)
  ) %>% 
  st_cast("MULTIPOLYGON")
```


## Africa - All

### Journals

```{r}
df_reduced_africa <-
  df %>%
  filter(continent == "Africa") %>%
  group_by(country) %>% 
  summarize(
    ojs_v2 = sum(ojs_v2, na.rm = T),
    ojs_v3 = sum(ojs_v3, na.rm = T)
  ) %>% 
  mutate(total = ojs_v2 + ojs_v3)

df_reduced_africa %>% 
  arrange(-total) %>% 
  datatable()
```

Totals for each column:

```{r}
df_reduced_africa %>%
  select(-country) %>% 
  summarize_all(sum, na.rm = TRUE) %>% 
  knitr::kable()
```


#### OJS v3 journals

```{r}
plot <-
  shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa, by = "country") %>% 
  mutate(
    ojs_v3 = replace_na(ojs_v3, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(text = country, fill = ojs_v3), size = 0.3) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_minimal() +
  labs(
    fill = "OJS v3 journals"
  )

ggplotly(plot)
```


#### OJS v2 journals

```{r}
plot <-
  shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa, by = "country") %>%  
  mutate(
    ojs_v2 = replace_na(ojs_v2, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(text = country, fill = ojs_v2), size = 0.3) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_minimal() +
  labs(
    fill = "OJS v2 journals"
  )

ggplotly(plot)
```


### Installations

```{r}
df_reduced_africa <-
  df %>%
  filter(continent == "Africa") %>% 
  distinct(repository_name, .keep_all = TRUE) %>% 
  group_by(country) %>% 
  summarize(
    ojs_v2 = sum(ojs_v2, na.rm = T),
    ojs_v3 = sum(ojs_v3, na.rm = T)
  ) %>%
  mutate(total = ojs_v2 + ojs_v3)

df_reduced_africa %>% 
  arrange(-total) %>% 
  datatable()
```

Totals for each column:

```{r}
df_reduced_africa %>%
  select(-country) %>% 
  summarize_all(sum, na.rm = TRUE) %>% 
  knitr::kable()
```


#### OJS v3 installations

```{r}
plot <-
  shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa, by = "country") %>% 
  mutate(
    ojs_v3 = replace_na(ojs_v3, 0)
  ) %>%
  ggplot() +
  geom_sf(aes(text = country, fill = ojs_v3), size = 0.3) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_minimal() +
  labs(
    fill = "OJS v3 installations"
  )

ggplotly(plot)
```

#### OJS v2 installations

```{r}
plot <-
  shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa, by = "country") %>%  
  mutate(
    ojs_v2 = replace_na(ojs_v2, 0)
  ) %>%
  ggplot() +
  geom_sf(aes(text = country, fill = ojs_v2), size = 0.3) +
  scale_fill_gradientn(
    breaks = seq(0, 15, 3),
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_minimal() +
  labs(
    fill = "OJS v2 installations"
  )

ggplotly(plot)
```


## Africa - Active

### Journals

```{r}
df_reduced_africa_act <-
  df_act %>%
  filter(continent == "Africa") %>%
  group_by(country) %>% 
  summarize(
    ojs_v2 = sum(ojs_v2, na.rm = T),
    ojs_v3 = sum(ojs_v3, na.rm = T)
  ) %>% 
  mutate(total = ojs_v2 + ojs_v3)

df_reduced_africa_act %>% 
  arrange(-total) %>% 
  datatable()
```

Totals for each column:

```{r}
df_reduced_africa_act %>%
  select(-country) %>% 
  summarize_all(sum, na.rm = TRUE) %>% 
  knitr::kable()
```


#### OJS v3 journals

```{r}
plot <-
  shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa_act, by = "country") %>% 
  mutate(
    ojs_v3 = replace_na(ojs_v3, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(text = country, fill = ojs_v3), size = 0.3) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_minimal() +
  labs(
    fill = "OJS v3 active\njournals"
  )

ggplotly(plot)
```


#### OJS v2 journals

```{r}
plot <-
  shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa_act, by = "country") %>%  
  mutate(
    ojs_v2 = replace_na(ojs_v2, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(text = country, fill = ojs_v2), size = 0.3) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_minimal() +
  labs(
    fill = "OJS v2 active\njournals"
  )

ggplotly(plot)
```


### Installations

```{r}
df_reduced_africa_act <-
  df_act %>%
  filter(continent == "Africa") %>% 
  distinct(repository_name, .keep_all = TRUE) %>% 
  group_by(country) %>% 
  summarize(
    ojs_v2 = sum(ojs_v2, na.rm = T),
    ojs_v3 = sum(ojs_v3, na.rm = T)
  ) %>%
  mutate(total = ojs_v2 + ojs_v3)

df_reduced_africa_act %>% 
  arrange(-total) %>% 
  datatable()
```

Totals for each column:

```{r}
df_reduced_africa_act %>%
  select(-country) %>% 
  summarize_all(sum, na.rm = TRUE) %>% 
  knitr::kable()
```


#### OJS v3 installations

```{r}
plot <-
  shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa_act, by = "country") %>% 
  mutate(
    ojs_v3 = replace_na(ojs_v3, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(text = country, fill = ojs_v3), size = 0.3) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_minimal() +
  labs(
    fill = "OJS v3 active\ninstallations"
  )

ggplotly(plot)
```

#### OJS v2 installations

```{r}
plot <-
  shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa_act, by = "country") %>%  
  mutate(
    ojs_v2 = replace_na(ojs_v2, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v2), size = 0.3) +
  scale_fill_gradientn(
    breaks = seq(0, 10, 2),
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_minimal() +
  labs(
    fill = "OJS v2 active\ninstallations"
  )

ggplotly(plot)
```


## Journals per OJS v2 installation in Africa


```{r}
df %>%
  filter(continent == "Africa", ojs_v2) %>% 
  count(country, domain, name = "count_all") %>% 
  left_join(
    df_act %>%
      filter(continent == "Africa", ojs_v2) %>% 
      count(country, domain, name = "count_active"),
    by = c("country", "domain")
  ) %>%
  mutate(
    count_active = replace_na(count_active, 0),
    dormant_journals = count_all - count_active
  ) %>% 
  rename(total_journals = count_all, active_journals = count_active, installation_domain = domain) %>% 
  arrange(-total_journals) %>% 
  datatable()
```
