---
title: "Beacon EDA for Africa"
author: "Saurabh Khanna"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 4
---

```{r setup, include=FALSE}
# knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

## Summary (ongoing)

+ All
  - Total OJS v2 journals found in Africa: 250
  - Total OJS v2 installations found in Africa: 39
+ Active
  - Total *active* OJS v2 journals found in Africa: 140
  - Total *active* OJS v2 installations found in Africa: 27 


```{r message=FALSE, warning=FALSE}
# Libraries
pacman::p_load(tidyverse, countrycode, sf, DT, htmltools, htmlwidgets, jsonlite, rgeolocate, urltools, lubridate, state, iptools, janitor)

# Data
df <- read_csv(here::here("data", "beacon.csv"))
shapefile <- read_sf(here::here("data/TM_WORLD_BORDERS_SIMPL-0.3.shp"))
df_pred2 <- read_csv(here::here("data", "predatory_msperlin.csv"))
tld <- read_csv(here::here("data", "tld-country.csv"))
tld_from_ip <- read_csv(here::here("data", "tld_from_ip.csv"))
df_act2019 <- read_csv(here::here("data/active", "beacon-2019.csv")) %>% select(oai_url, version, repository_name, issn, country, set_spec)
df_act2018 <- read_csv(here::here("data/active", "beacon-2018.csv")) %>% select(oai_url, version, repository_name, issn, country, set_spec)
df_act2017 <- read_csv(here::here("data/active", "beacon-2017.csv")) %>% select(oai_url, version, repository_name, issn, country, set_spec)
df_act <-
  bind_rows(
    df_act2017, df_act2018, df_act2019,
    .id = "year"
  ) %>% 
  mutate(
    year = as.integer(year) + 2016L
  ) %>% 
  arrange(desc(year), oai_url, version, repository_name, issn, country, set_spec) %>% 
  distinct(oai_url, version, repository_name, issn, country, set_spec, .keep_all = T)

rm(df_act2017, df_act2018, df_act2019)
```



```{r}
#df %>% distinct(oai_url) summarize_all(~ sum(is.na(.)))
df <- 
  bind_cols(
    df,
    df %>% pull(oai_url) %>% domain() %>% tld_extract()
  ) %>% 
  left_join(tld_from_ip, by = "domain") %>% 
  mutate(
    tld = if_else(!is.na(tld_from_ip), tld_from_ip, tld)
  ) %>% 
  left_join(tld, by = "tld")

df_act <- 
  bind_cols(
    df_act,
    df_act %>% pull(oai_url) %>% domain() %>% tld_extract()
  ) %>% 
  left_join(tld_from_ip, by = "domain") %>% 
  mutate(
    tld = if_else(!is.na(tld_from_ip), tld_from_ip, tld)
  ) %>%
  left_join(tld, by = "tld")
```


```{r}
### Mapping countries to continents
df <-
  df %>% 
  mutate(
    country = if_else(!is.na(country_clean), country_clean, country),
    ojs_v2 = str_detect(version, "^ojs2/2"),
    ojs_v3 = str_detect(version, "^ojs2/3"),
    version_clean = case_when(
      ojs_v2 ~ "Version 2",
      ojs_v3 ~ "Version 3",
      TRUE ~ "Other"
    )
  )

continents <-
  df %>% 
  pull(country) %>% 
  countrycode(origin = "country.name", destination = "continent")

df <- 
  df %>%
  bind_cols(continents) %>% 
  rename(continent = `...20`)

df_act <-
  df_act %>% 
  mutate(
    country = if_else(!is.na(country_clean), country_clean, country),
    ojs_v2 = str_detect(version, "^ojs2/2"),
    ojs_v3 = str_detect(version, "^ojs2/3"),
    version_clean = case_when(
      ojs_v2 ~ "Version 2",
      ojs_v3 ~ "Version 3",
      TRUE ~ "Other"
    )
  )

continents <-
  df_act %>% 
  pull(country) %>% 
  countrycode(origin = "country.name", destination = "continent")

df_act <- 
  df_act %>%
  bind_cols(continents) %>% 
  rename(continent = `...15`)
```


## Africa - All

### Journals

```{r}
df_reduced_africa <-
  df %>%
  filter(continent == "Africa") %>%
  group_by(country) %>% 
  summarize(
    ojs_v2 = sum(ojs_v2, na.rm = T),
    ojs_v3 = sum(ojs_v3, na.rm = T),
    #records = sum(total_record_count, na.rm = T)
  ) %>% 
  mutate(total = ojs_v2 + ojs_v3)

df_reduced_africa %>% 
  arrange(-total) %>% 
  datatable()
```

Totals for each column:

```{r}
df_reduced_africa %>%
  select(-country) %>% 
  summarize_all(sum, na.rm = TRUE) %>% 
  knitr::kable()
```


#### OJS v3 journals

```{r}
shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa, by = "country") %>% 
  mutate(
    ojs_v3 = replace_na(ojs_v3, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v3), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(ojs_v3 >= 3),
    aes(lon, lat, label = ojs_v3),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "OJS v3 journals"
  )
```


#### OJS v2 journals

```{r}
shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa, by = "country") %>%  
  mutate(
    ojs_v2 = replace_na(ojs_v2, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v2), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(ojs_v2 > 0),
    aes(lon, lat, label = ojs_v2),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "OJS v2 journals"
  )
```


### Installations

```{r}
df_reduced_africa <-
  df %>%
  filter(continent == "Africa") %>% 
  distinct(repository_name, .keep_all = TRUE) %>% 
  group_by(country) %>% 
  summarize(
    ojs_v2 = sum(ojs_v2, na.rm = T),
    ojs_v3 = sum(ojs_v3, na.rm = T),
    #records = sum(total_record_count, na.rm = T)
  ) %>%
  mutate(total = ojs_v2 + ojs_v3)

df_reduced_africa %>% 
  arrange(-total) %>% 
  datatable()
```

Totals for each column:

```{r}
df_reduced_africa %>%
  select(-country) %>% 
  summarize_all(sum, na.rm = TRUE) %>% 
  knitr::kable()
```


#### OJS v3 installations

```{r}
shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa, by = "country") %>% 
  mutate(
    ojs_v3 = replace_na(ojs_v3, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v3), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(ojs_v3 >= 3),
    aes(lon, lat, label = ojs_v3),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "OJS v3 installations"
  )
```

#### OJS v2 installations

```{r}
shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa, by = "country") %>%  
  mutate(
    ojs_v2 = replace_na(ojs_v2, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v2), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(ojs_v2 > 0),
    aes(lon, lat, label = ojs_v2),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "OJS v2 installations"
  )
```


## Africa - Active

### Journals

```{r}
df_reduced_africa_act <-
  df_act %>%
  filter(continent == "Africa") %>%
  group_by(country) %>% 
  summarize(
    ojs_v2 = sum(ojs_v2, na.rm = T),
    ojs_v3 = sum(ojs_v3, na.rm = T),
    #records = sum(total_record_count, na.rm = T)
  ) %>% 
  mutate(total = ojs_v2 + ojs_v3)

df_reduced_africa_act %>% 
  arrange(-total) %>% 
  datatable()
```

Totals for each column:

```{r}
df_reduced_africa_act %>%
  select(-country) %>% 
  summarize_all(sum, na.rm = TRUE) %>% 
  knitr::kable()
```


#### OJS v3 journals

```{r}
shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa_act, by = "country") %>% 
  mutate(
    ojs_v3 = replace_na(ojs_v3, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v3), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(ojs_v3 >= 3),
    aes(lon, lat, label = ojs_v3),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "OJS v3 active\njournals"
  )
```


#### OJS v2 journals

```{r}
shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa_act, by = "country") %>%  
  mutate(
    ojs_v2 = replace_na(ojs_v2, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v2), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(ojs_v2 > 0),
    aes(lon, lat, label = ojs_v2),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "OJS v2 active\njournals"
  )
```


### Installations

```{r}
df_reduced_africa_act <-
  df_act %>%
  filter(continent == "Africa") %>% 
  distinct(repository_name, .keep_all = TRUE) %>% 
  group_by(country) %>% 
  summarize(
    ojs_v2 = sum(ojs_v2, na.rm = T),
    ojs_v3 = sum(ojs_v3, na.rm = T),
    #records = sum(total_record_count, na.rm = T)
  ) %>%
  mutate(total = ojs_v2 + ojs_v3)

df_reduced_africa_act %>% 
  arrange(-total) %>% 
  datatable()
```

Totals for each column:

```{r}
df_reduced_africa_act %>%
  select(-country) %>% 
  summarize_all(sum, na.rm = TRUE) %>% 
  knitr::kable()
```


#### OJS v3 installations

```{r}
shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa_act, by = "country") %>% 
  mutate(
    ojs_v3 = replace_na(ojs_v3, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v3), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(ojs_v3 >= 1),
    aes(lon, lat, label = ojs_v3),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "OJS v3 active\ninstallations"
  )
```

#### OJS v2 installations

```{r}
shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa_act, by = "country") %>%  
  mutate(
    ojs_v2 = replace_na(ojs_v2, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = as.integer(ojs_v2)), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(ojs_v2 > 0),
    aes(lon, lat, label = ojs_v2),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "OJS v2 active\ninstallations"
  )
```


## Journals per OJS v2 installation

### All

```{r}
df %>%
  filter(continent == "Africa", ojs_v2) %>% 
  count(country, domain, name = "count") %>% 
  arrange(-count) %>% 
  datatable()
```


### Active

```{r}
df_act %>%
  filter(continent == "Africa", ojs_v2) %>% 
  count(country, domain, name = "count") %>% 
  arrange(-count) %>% 
  datatable()
```

