---
title: "Beacon EDA"
author: "Saurabh Khanna"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 4
---

```{r setup, include=FALSE}
# knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

## Beacon EDA

Summary (ongoing):

* Total OJS v2 journals found in Africa: 250
* Total OJS v2 installations found in Africa: 39
* Total OJS v2 journals in Africa found on Beall's list: 1


```{r message=FALSE, warning=FALSE}
# Libraries
pacman::p_load(tidyverse, countrycode, sf, DT, htmltools, htmlwidgets, jsonlite, rgeolocate, urltools, lubridate, state)

# Data
df <- read_csv(here::here("data", "beacon.csv"))
shapefile <- read_sf(here::here("data/TM_WORLD_BORDERS_SIMPL-0.3.shp"))
df_pred2 <- read_csv(here::here("data", "predatory_msperlin.csv"))
tld <- read_csv(here::here("data", "tld-country.csv"))
```


```{r}
#df %>% distinct(oai_url) summarize_all(~ sum(is.na(.)))
df <- 
  bind_cols(
    df,
    df %>% pull(oai_url) %>% domain() %>% tld_extract()
  ) %>% 
  left_join(tld, by = "tld")
```


## Country cleaning

Countries cleaned based on ISO3166 codes.

* Countries added for 11916 journals
* Countries mismatched for 660 journals (shared with Alec)
* Country still missing for 4549 journals

```{r eval=F}
df %>%
  select(repository_name, contains("country")) %>% 
  filter(is.na(country) & !is.na(country_clean))
```


```{r eval=F}
df %>% 
  filter(country != country_clean) %>% 
  relocate(repository_name, country, country_clean, oai_url)
```

```{r}
### Mapping countries to continents
df <-
  df %>% 
  mutate(
    country = if_else(!is.na(country_clean), country_clean, country),
    ojs_v2 = str_detect(version, "^ojs2/2"),
    ojs_v3 = str_detect(version, "^ojs2/3"),
    version_clean = case_when(
      ojs_v2 ~ "Version 2",
      ojs_v3 ~ "Version 3",
      TRUE ~ "Other"
    )
    #years = (earliest_datestamp %--% last_beacon) / dyears(1),
    #records_per_year = total_record_count / years,
    #active = records_per_year >= 5
  )

continents <-
  df %>% 
  pull(country) %>% 
  countrycode(origin = "country.name", destination = "continent")

df <- 
  df %>%
  bind_cols(continents) %>% 
  rename(continent = `...19`)
```


## Africa

### Journals

```{r}
df_reduced_africa <-
  df %>%
  filter(continent == "Africa") %>%
  group_by(country) %>% 
  summarize(
    ojs_v2 = sum(ojs_v2, na.rm = T),
    ojs_v3 = sum(ojs_v3, na.rm = T),
    #records = sum(total_record_count, na.rm = T)
  ) %>% 
  mutate(total = ojs_v2 + ojs_v3)

df_reduced_africa %>% 
  arrange(-total) %>% 
  datatable()
```

#### OJS v2 journals

```{r}
shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa, by = "country") %>%  
  mutate(
    ojs_v2 = replace_na(ojs_v2, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v2), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(ojs_v2 > 0),
    aes(lon, lat, label = ojs_v2),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "OJS v2 journals"
  )
```


#### OJS v3 journals

```{r}
shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa, by = "country") %>% 
  mutate(
    ojs_v3 = replace_na(ojs_v3, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v3), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(ojs_v3 >= 3),
    aes(lon, lat, label = ojs_v3),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "OJS v3 journals"
  )
```


### Installations

```{r}
df_reduced_africa <-
  df %>%
  filter(continent == "Africa") %>% 
  distinct(repository_name, .keep_all = TRUE) %>% 
  group_by(country) %>% 
  summarize(
    ojs_v2 = sum(ojs_v2, na.rm = T),
    ojs_v3 = sum(ojs_v3, na.rm = T),
    #records = sum(total_record_count, na.rm = T)
  ) %>%
  mutate(total = ojs_v2 + ojs_v3)

df_reduced_africa %>% 
  arrange(-total) %>% 
  datatable()
```

#### OJS v2 installations

```{r}
shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa, by = "country") %>%  
  mutate(
    ojs_v2 = replace_na(ojs_v2, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v2), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(ojs_v2 > 0),
    aes(lon, lat, label = ojs_v2),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "OJS v2 installations"
  )
```


#### OJS v3 installations

```{r}
shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa, by = "country") %>% 
  mutate(
    ojs_v3 = replace_na(ojs_v3, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v3), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(ojs_v3 >= 3),
    aes(lon, lat, label = ojs_v3),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "OJS v3 installations"
  )
```


### Merging with scraped Beall's list

Seeing just [one match](http://journals.uniosun.edu.ng/){target="_blank"} from Africa for now, could be because the country variable needs to be cleaned further (currently includes US states being entered as countries etc.).

```{r}
df_pred2 %>%
  inner_join(df, by = "issn") %>%
  mutate(continent = if_else(is.na(continent), "Americas", continent)) %>% 
  count(continent, name = "count") %>% 
  arrange(-count) %>% 
  knitr::kable()
```


### URLs to scrape for Africa

```{r}
df %>%
  filter(continent == "Africa", ojs_v2) %>% 
  count(country, domain, name = "count") %>% 
  arrange(country, -count) %>% 
  datatable()
```

## Global stats

### Journals

```{r}
canada.states <- 
  c("Alberta", "British Columbia", "Labrador", "Manitoba", "New Brunswick", "Newfoundland", "Nova Scotia", "Nunavut", "North West Terr.", "Ontario", "Prince Edward Is.", "Québec (Province)", "Saskatchewan", "Yukon")

df_reduced <-
  df %>%
  drop_na(country) %>% 
  mutate(
    country = if_else(str_detect(country, "China"), "China", country),
    country = if_else(str_detect(country, "England"), "United Kingdom", country),
    country = if_else(str_detect(country, "Russia|Soviet Union"), "Russia", country),
    country = if_else(str_detect(country, "Palestine"), "Palestine", country),
    country = if_else(str_detect(country, "United States|New York"), "United States", country),
    country = if_else(country %in% state.name, "United States", country),
    country = if_else(country %in% canada.states, "Canada", country)
  ) %>% 
  group_by(country) %>% 
  summarize(
    ojs_v2 = sum(ojs_v2, na.rm = T),
    ojs_v3 = sum(ojs_v3, na.rm = T),
    #records = sum(total_record_count, na.rm = T)
  ) %>% 
  mutate(
    total = ojs_v2 + ojs_v3
  )

df_reduced %>% 
  arrange(-total) %>% 
  datatable()
```

#### Total OJS journals

```{r, out.width="100%", out.height="100%"}
labels <- function(x) {
  if_else(x < 500, as.character(x), "500+")
}

shapefile %>% 
  janitor::clean_names() %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country),
    country = if_else(country == "Viet Nam", "Vietnam", country),
    country = if_else(str_detect(country, "Iran"), "Iran", country),
  ) %>% 
  left_join(df_reduced, by = "country") %>% 
  mutate(
    total = replace_na(total, 0),
    total = pmin(total, 500)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = total), size = 0.3) +
  scale_fill_gradientn(
    breaks = seq(0, 500, 250),
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd"),
    labels = labels
  ) +
  theme_void() +
  theme(legend.position = "bottom") +
  labs(
    fill = "Total OJS journals"
  )
```


#### OJS v2 journals

```{r, out.width="100%", out.height="100%"}
labels <- function(x) {
  if_else(x < 200, as.character(x), "200+")
}

shapefile %>% 
  janitor::clean_names() %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country),
    country = if_else(country == "Viet Nam", "Vietnam", country),
    country = if_else(str_detect(country, "Iran"), "Iran", country),
  ) %>% 
  left_join(df_reduced, by = "country") %>% 
  mutate(
    ojs_v2 = replace_na(ojs_v2, 0),
    ojs_v2 = pmin(ojs_v2, 200)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v2), size = 0.3) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd"),
    labels = labels
  ) +
  theme_void() +
  theme(legend.position = "bottom") +
  labs(
    fill = "OJS v2 journals"
  )
```


#### OJS v3 journals

```{r, out.width="100%", out.height="100%"}
labels <- function(x) {
  if_else(x < 500, as.character(x), "500+")
}

shapefile %>% 
  janitor::clean_names() %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country),
    country = if_else(country == "Viet Nam", "Vietnam", country),
    country = if_else(str_detect(country, "Iran"), "Iran", country),
  ) %>% 
  left_join(df_reduced, by = "country") %>% 
  mutate(
    ojs_v3 = replace_na(ojs_v3, 0),
    ojs_v3 = pmin(ojs_v3, 500)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v3), size = 0.3) +
  scale_fill_gradientn(
    breaks = seq(0, 500, 250),
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd"),
    labels = labels
  ) +
  theme_void() +
  theme(legend.position = "bottom") +
  labs(
    fill = "OJS v3 journals"
  )
```

### Installations

```{r, out.width="100%", out.height="100%"}
df_reduced <-
  df %>%
  drop_na(country) %>% 
  distinct(repository_name, .keep_all = T) %>% 
  mutate(
    country = if_else(str_detect(country, "China"), "China", country),
    country = if_else(str_detect(country, "England"), "United Kingdom", country),
    country = if_else(str_detect(country, "Russia|Soviet Union"), "Russia", country),
    country = if_else(str_detect(country, "Palestine"), "Palestine", country),
    country = if_else(str_detect(country, "United States|New York"), "United States", country),
    country = if_else(country %in% state.name, "United States", country),
    country = if_else(country %in% canada.states, "Canada", country)
  ) %>% 
  group_by(country) %>% 
  summarize(
    ojs_v2 = sum(ojs_v2, na.rm = T),
    ojs_v3 = sum(ojs_v3, na.rm = T)
  ) %>% 
  mutate(
    total = ojs_v2 + ojs_v3
  )

df_reduced %>% 
  arrange(-total) %>% 
  datatable()
```

#### Total OJS installations

```{r, out.width="100%", out.height="100%"}
labels <- function(x) {
  if_else(x < 100, as.character(x), "100+")
}

shapefile %>% 
  janitor::clean_names() %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country),
    country = if_else(country == "Viet Nam", "Vietnam", country),
    country = if_else(str_detect(country, "Iran"), "Iran", country),
  ) %>% 
  left_join(df_reduced, by = "country") %>% 
  mutate(
    total = replace_na(total, 0),
    total = pmin(total, 100)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = total), size = 0.3) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd"),
    labels = labels
  ) +
  theme_void() +
  theme(legend.position = "bottom") +
  labs(
    fill = "Total OJS installations"
  )
```


#### OJS v2 installations

```{r, out.width="100%", out.height="100%"}
labels <- function(x) {
  if_else(x < 100, as.character(x), "100+")
}

shapefile %>% 
  janitor::clean_names() %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country),
    country = if_else(country == "Viet Nam", "Vietnam", country),
    country = if_else(str_detect(country, "Iran"), "Iran", country),
  ) %>% 
  left_join(df_reduced, by = "country") %>% 
  mutate(
    ojs_v2 = replace_na(ojs_v2, 0),
    ojs_v2 = pmin(ojs_v2, 100)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v2), size = 0.3) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd"),
    labels = labels
  ) +
  theme_void() +
  theme(legend.position = "bottom") +
  labs(
    fill = "OJS v2 installations"
  )
```


#### OJS v3 installations

```{r, out.width="100%", out.height="100%"}
labels <- function(x) {
  if_else(x < 100, as.character(x), "100+")
}

shapefile %>% 
  janitor::clean_names() %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country),
    country = if_else(country == "Viet Nam", "Vietnam", country),
    country = if_else(str_detect(country, "Iran"), "Iran", country),
  ) %>% 
  left_join(df_reduced, by = "country") %>% 
  mutate(
    ojs_v3 = replace_na(ojs_v3, 0),
    ojs_v3 = pmin(ojs_v3, 100)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v3), size = 0.3) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd"),
    labels = labels
  ) +
  theme_void() +
  theme(legend.position = "bottom") +
  labs(
    fill = "OJS v3 installations"
  )
```
