---
title: "Beacon EDA"
author: "Saurabh Khanna"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
# knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

## Beacon EDA

Summary (ongoing):

* Total OJS v2 installations found in Africa: 264
* Total Active OJS v2 installations found in Africa: 158
* Total OJS v2 installations in Africa found on Beall's list: 1


```{r message=FALSE, warning=FALSE}
# Libraries
pacman::p_load(tidyverse, countrycode, sf, DT, htmltools, htmlwidgets, jsonlite, rgeolocate, urltools, lubridate)

# Data
df <- read_csv(here::here("data", "beacon.csv"))
shapefile <- read_sf(here::here("data/TM_WORLD_BORDERS_SIMPL-0.3.shp"))
df_pred2 <- read_csv(here::here("data", "predatory_msperlin.csv"))
tld <- read_csv(here::here("data", "tld-country.csv"))
```

```{r}
#df %>% distinct(oai_url) summarize_all(~ sum(is.na(.)))
df <- 
  bind_cols(
    df,
    df %>% pull(oai_url) %>% domain() %>% tld_extract()
  ) %>% 
  left_join(tld, by = "tld")
```


### Country cleaning

Countries cleaned based on country code top level domains. These codes are also the same as [ISO 3166 codes](https://en.wikipedia.org/wiki/ISO_3166-1_alpha-2){target="_blank"}.

* Countries added for 14461 observations
* Countries mismatched for 773 observations (shared with Alec).
* Country still missing for 5639 observations.

```{r eval=F}
df %>%
  select(repository_name, contains("country")) %>% 
  filter(is.na(country) & !is.na(country_clean)) %>% 
  distinct() %>% 
  datatable()
```


```{r eval=F}
df %>% 
  #select(repository_name, contains("country")) %>% 
  filter(country != country_clean) %>% 
  relocate(id, repository_name, country, country_clean, oai_url)
```

```{r}
### Mapping countries to continents
df <-
  df %>% 
  mutate(
    country = if_else(!is.na(country_clean), country_clean, country),
    ojs_v2 = str_detect(version, "^ojs2/2"),
    ojs_v3 = str_detect(version, "^ojs2/3"),
    years = (earliest_datestamp %--% last_beacon) / dyears(1),
    records_per_year = total_record_count / years,
    active = records_per_year >= 5
  )

continents <-
  df %>% 
  pull(country) %>% 
  countrycode(origin = "country.name", destination = "continent")

df <- 
  df %>%
  bind_cols(continents) %>% 
  rename(continent = `...27`)
```


### OJS installations for Africa

```{r}
df_reduced_africa <-
  df %>%
  filter(continent == "Africa") %>%
  group_by(country) %>% 
  summarize(
    ojs_v2 = sum(ojs_v2, na.rm = T),
    ojs_v3 = sum(ojs_v3, na.rm = T),
    records = sum(total_record_count, na.rm = T)
  )

df_reduced_africa %>% 
  arrange(-ojs_v2) %>% 
  datatable()
```


### Number of OJS v2 installations

```{r}
shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "C么te d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa, by = "country") %>%  
  mutate(
    ojs_v2 = replace_na(ojs_v2, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v2), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(ojs_v2 > 0),
    aes(lon, lat, label = ojs_v2),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "OJS v2 installations"
  )
```


### Number of OJS v3 installations

```{r}
shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "C么te d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa, by = "country") %>% 
  mutate(
    ojs_v3 = replace_na(ojs_v3, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v3), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(ojs_v3 >= 3),
    aes(lon, lat, label = ojs_v3),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "OJS v3 installations"
  )
```


### Number of total records

```{r}
shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "C么te d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_reduced_africa, by = "country") %>% 
  mutate(
    records = replace_na(records, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = records), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(records >= 300),
    aes(lon, lat, label = records),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "Number of records"
  )
```

## Active OJS v2 journals in Africa (Draft)

Current defining an OJS v2 journal as `active` if it publishes at least 5 records/articles per year. The interval considered begins from the earliest timestamp recorded and ends at the latest beacon timestamp.


```{r}
df_plot <-
  df %>% 
  filter(ojs_v2, continent == "Africa") %>% 
  group_by(country) %>% 
  summarize(
    ojs_v2 = sum(n(), na.rm = T),
    ojs_v2_active = sum(active, na.rm = T)
  ) %>% 
  arrange(-ojs_v2)

datatable(df_plot)

shapefile %>% 
  janitor::clean_names() %>% 
  filter(region == 2) %>%
  rename(country = name) %>% 
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "C么te d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country)
  ) %>% 
  left_join(df_plot, by = "country") %>%  
  mutate(
    ojs_v2_active = replace_na(ojs_v2_active, 0)
  ) %>% 
  ggplot() +
  geom_sf(aes(fill = ojs_v2_active), size = 0.3) +
  ggrepel::geom_label_repel(
    data = . %>% filter(ojs_v2_active > 0),
    aes(lon, lat, label = ojs_v2_active),
    nudge_x = -8
  ) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_void() +
  labs(
    fill = "OJS v2 active\ninstallations"
  )
```



## Merging with scraped Beall's list

Seeing just [one match](http://journals.uniosun.edu.ng/){target="_blank"} from Africa for now, could be because the country variable needs to be cleaned further (currently includes US states being entered as countries etc.).

```{r}
df_pred2 %>%
  inner_join(df, by = "issn") %>%
  count(continent, name = "count") %>% 
  mutate(continent = if_else(is.na(continent), "North America", continent)) %>% 
  arrange(-count) %>% 
  knitr::kable()


# df_pred2 %>%
#   inner_join(df, by = "issn") %>%
#   drop_na(country) %>% 
#   group_by(country) %>% 
#   summarize(
#     `OJSv2 Installations 'listed' as predatory` = sum(ojs_v2, na.rm = T),
#     `OJSv3 Installations 'listed' as predatory` = sum(ojs_v3, na.rm = T)
#   ) %>% 
#   arrange(desc(`OJSv2 Installations 'listed' as predatory`)) %>% 
#   datatable()
```

