---
title: "OJS Research Dashboard"
#author: "Saurabh Khanna"
date: "Updated: `r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 4
---

```{r setup, include=FALSE}
# knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.retina = 4)
```


```{r message=FALSE, warning=FALSE}
# Libraries
pacman::p_load(tidyverse, countrycode, sf, state, htmltools, htmlwidgets, urltools, lubridate, janitor, plotly)

# Data
df <- read_csv(here::here("data", "beacon.csv"))
shapefile <- read_sf(here::here("data/TM_WORLD_BORDERS_SIMPL-0.3.shp"))
tld <- read_csv(here::here("data", "tld-country.csv"))
tld_from_ip <- read_csv(here::here("data", "tld_from_ip.csv"))
df_act2019 <- read_csv(here::here("data/active", "beacon-2019.csv")) %>% select(oai_url, version, repository_name, issn, country, set_spec)
df_act2018 <- read_csv(here::here("data/active", "beacon-2018.csv")) %>% select(oai_url, version, repository_name, issn, country, set_spec)
df_act2017 <- read_csv(here::here("data/active", "beacon-2017.csv")) %>% select(oai_url, version, repository_name, issn, country, set_spec)
df_act <-
  bind_rows(
    df_act2017, df_act2018, df_act2019,
    .id = "year"
  ) %>% 
  mutate(
    year = as.integer(year) + 2016L
  ) %>% 
  arrange(desc(year), oai_url, version, repository_name, issn, country, set_spec) %>% 
  distinct(oai_url, version, repository_name, issn, country, set_spec, .keep_all = T)

canada.states <- 
  c("Alberta", "British Columbia", "Labrador", "Manitoba", "New Brunswick", "Newfoundland", "Nova Scotia", "Nunavut", "North West Terr.", "Ontario", "Prince Edward Is.", "Québec (Province)", "Saskatchewan", "Yukon")

rm(df_act2017, df_act2018, df_act2019)
```


```{r}
# correcting some oai urls
df <- df %>% mutate(oai_url = if_else(str_detect(oai_url, "^//"), str_c("http:", oai_url), oai_url))
df_act <- df_act %>% mutate(oai_url = if_else(str_detect(oai_url, "^//"), str_c("http:", oai_url), oai_url))
```


```{r}
df <- 
  bind_cols(
    df,
    df %>% pull(oai_url) %>% domain() %>% tld_extract()
  ) %>% 
  left_join(tld_from_ip, by = "domain") %>%
  mutate(
    tld = if_else(!is.na(tld_from_ip), tld_from_ip, tld)
  ) %>%
  left_join(tld, by = "tld")

df_act <- 
  bind_cols(
    df_act,
    df_act %>% pull(oai_url) %>% domain() %>% tld_extract()
  ) %>% 
  left_join(tld_from_ip, by = "domain") %>%
  mutate(
    tld = if_else(!is.na(tld_from_ip), tld_from_ip, tld)
  ) %>%
  left_join(tld, by = "tld")
```


```{r}
# Mapping countries to continents
df <-
  df %>% 
  mutate(
    country = if_else(is.na(country), country_clean, country),
    ojs_v2 = str_detect(version, "^ojs2/2"),
    ojs_v3 = str_detect(version, "^ojs2/3"),
    version_clean = case_when(
      ojs_v2 ~ "Version 2",
      ojs_v3 ~ "Version 3",
      TRUE ~ "Other"
    )
  ) %>% 
  mutate(
    country = if_else(str_detect(country, "China"), "China", country),
    country = if_else(str_detect(country, "Armenia"), "Armenia", country),
    country = if_else(str_detect(country, "Georgia"), "Georgia", country),
    country = if_else(str_detect(country, "Australia|New South Wales|Queensland|Victoria"), "Australia", country),
    country = if_else(str_detect(country, "England"), "United Kingdom", country),
    country = if_else(str_detect(country, "Russia|Soviet Union"), "Russia", country),
    country = if_else(str_detect(country, "Palestine"), "Palestine", country),
    country = if_else(country == "Korea (South)", "South Korea", country),
    country = if_else(country == "Washington (State)", "United States", country),
    country = if_else(str_detect(country, "United States|New York|District of Columbia"), "United States", country),
    country = if_else(country %in% state.name, "United States", country),
    country = if_else(country %in% canada.states, "Canada", country)
  )

continents <-
  df %>%
  pull(country) %>% 
  countrycode(origin = "country.name", destination = "continent")

df <- 
  df %>%
  bind_cols(continents) %>% 
  rename(continent = `...22`)

df_act <-
  df_act %>% 
  mutate(
    country = if_else(is.na(country), country_clean, country),
    ojs_v2 = str_detect(version, "^ojs2/2"),
    ojs_v3 = str_detect(version, "^ojs2/3"),
    version_clean = case_when(
      ojs_v2 ~ "Version 2",
      ojs_v3 ~ "Version 3",
      TRUE ~ "Other"
    )
  ) %>% 
  mutate(
    country = if_else(str_detect(country, "China"), "China", country),
    country = if_else(str_detect(country, "Armenia"), "Armenia", country),
    country = if_else(str_detect(country, "Georgia"), "Georgia", country),
    country = if_else(str_detect(country, "Australia|New South Wales|Queensland|Victoria"), "Australia", country),
    country = if_else(str_detect(country, "England"), "United Kingdom", country),
    country = if_else(str_detect(country, "Russia|Soviet Union"), "Russia", country),
    country = if_else(str_detect(country, "Palestine"), "Palestine", country),
    country = if_else(country == "Korea (South)", "South Korea", country),
    country = if_else(country == "Washington (State)", "United States", country),
    country = if_else(str_detect(country, "United States|New York|District of Columbia"), "United States", country),
    country = if_else(country %in% state.name, "United States", country),
    country = if_else(country %in% canada.states, "Canada", country)
  )

continents <-
  df_act %>% 
  pull(country) %>% 
  countrycode(origin = "country.name", destination = "continent")

df_act <- 
  df_act %>%
  bind_cols(continents) %>% 
  rename(continent = `...15`)

rm(tld, tld_from_ip)

# merging morocco and western sahara
shapefile <-
  shapefile %>% 
  clean_names() %>% 
  mutate(
    name = if_else(name == "Western Sahara", "Morocco", name)
  ) %>%
  arrange(name) %>% 
  group_by(name) %>% 
  summarize(
    geometry = st_union(geometry),
    lat = first(lat),
    lon = first(lon),
    region = first(region),
    subregion = first(subregion)
  ) %>% 
  st_cast("MULTIPOLYGON")
```



```{r}
# creating grouped dfs
df_world <-
  df %>%
  drop_na(country) %>%   
  group_by(country, continent) %>% 
  summarize(
    ojs_v2 = sum(ojs_v2, na.rm = T),
    ojs_v3 = sum(ojs_v3, na.rm = T)
  ) %>% 
  ungroup() %>% 
  transmute(
    country,
    continent,
    ojs_v2,
    ojs_v3,
    total = ojs_v2 + ojs_v3
  )

df_world_act <-
  df_act %>%
  drop_na(country) %>% 
  group_by(country) %>% 
  summarize(
    ojs_v2_active = sum(ojs_v2, na.rm = T),
    ojs_v3_active = sum(ojs_v3, na.rm = T)
  ) %>% 
  transmute(
    country, 
    ojs_v2_active,
    ojs_v3_active,
    total_active = ojs_v2_active + ojs_v3_active
  )

df_world <-
  df_world %>% 
  left_join(df_world_act, by = "country") %>% 
  mutate(
    total = replace_na(total, 0),
    total_active = replace_na(total_active, 0),
    total = if_else(total < total_active, total_active, total),
    ojs_v2 = replace_na(ojs_v2, 0),
    ojs_v2_active = replace_na(ojs_v2_active, 0),
    ojs_v2 = if_else(ojs_v2 < ojs_v2_active, ojs_v2_active, ojs_v2),
    ojs_v3 = replace_na(ojs_v3, 0),
    ojs_v3_active = replace_na(ojs_v3_active, 0),
    ojs_v3 = if_else(ojs_v3 < ojs_v3_active, ojs_v3_active, ojs_v3)
  )

rm(df_world_act)
```


```{r}
# creating installation df
df_world_install <-
  df %>%
  drop_na(country) %>%   
  group_by(country, continent, domain) %>% 
  summarize(ojs_v2 = sum(ojs_v2, na.rm = T)) %>% 
  ungroup()

df_world_install_act <-
  df_act %>%
  drop_na(country) %>%   
  group_by(country, domain) %>% 
  summarize(ojs_v2_active = sum(ojs_v2, na.rm = T)) %>% 
  ungroup()


df_world_install <-
  df_world_install %>% 
  left_join(df_world_install_act, by = c("country", "domain")) %>% 
  mutate(
    ojs_v2 = replace_na(ojs_v2, 0),
    ojs_v2_active = replace_na(ojs_v2_active, 0),
    ojs_v2 = if_else(ojs_v2 < ojs_v2_active, ojs_v2_active, ojs_v2)
  )

rm(df_world_install_act)
```


---

### Global Use of OJS by Version, 2017-19
**Active journals using OJS (5 records/year): 2017, 2018 or 2019**

Total count: 11,572 active (26,374 present)

OJS 3: 7,425 active (18,741 present)

OJS 2: 4,147 active (7,633 present)

```{r, eval = F}
# totals
df_world %>% 
  select(ojs_total_active = total_active, ojs_total = total, ojs_v3_active, ojs_v3, ojs_v2_active, ojs_v2) %>% 
  summarize_all(sum, na.rm = TRUE)
```


```{r, out.width="100%"}
plot <-
  shapefile %>% 
  janitor::clean_names() %>%
  rename(country = name) %>%
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country),
    country = if_else(country == "Viet Nam", "Vietnam", country),
    country = if_else(str_detect(country, "Iran"), "Iran", country),
    country = if_else(str_detect(country, "Korea, Republic of"), "South Korea", country),
    country = if_else(str_detect(country, "Korea, Democratic People's Republic of"), "North Korea", country),
    country = if_else(str_detect(country, "Surinam"), "Surinam", country)
  ) %>%
  left_join(df_world, by = "country") %>% 
  filter(country != "Antarctica") %>% 
  mutate(
    total = replace_na(total, 0),
    total_active = replace_na(total_active, 0),
    ojs_v2 = replace_na(ojs_v2, 0),
    ojs_v2_active = replace_na(ojs_v2_active, 0),
    ojs_v3 = replace_na(ojs_v3, 0),
    ojs_v3_active = replace_na(ojs_v3_active, 0),
    subtext1 = str_c("Journals: ", total_active, " active (", total, " present)"),
    subtext2 = str_c("V3: ", ojs_v3_active, " active (", ojs_v3, " present)"),
    subtext3 = str_c("V2: ", ojs_v2_active, " active (", ojs_v2, " present)"),
    hover_text = str_c(country, subtext1, subtext2, subtext3, sep = "\n"),
    total_active = pmin(total_active, 500)
  ) %>%
  ggplot() +
  geom_sf(aes(fill = total_active, text = hover_text), size = 0.3, show.legend = FALSE) +
  scale_fill_gradientn(
    breaks = seq(0, 500, 250),
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_minimal()

ggplotly(plot, tooltip = "hover_text") %>% 
  layout(
    xaxis = list(autorange = TRUE), 
    yaxis = list(autorange = TRUE)
  )
```

```{r}
df_world %>% 
  arrange(-total_active) %>% 
  select(Country = country, Active = total_active, Present = total, `V3 active` = ojs_v3_active, `V3 present` = ojs_v3, `V2 active` = ojs_v2_active, `V2 present` = ojs_v2) %>% 
  DT::datatable()
```


---

### African Use of OJS by Version, 2017-19
**Active journals using OJS (5 records/year): 2017, 2018 or 2019**

Total count: 295 active (759 present)

OJS 3: 155 active (516 present)

OJS 2: 140 active (243 present)

```{r, eval = F}
# totals
df_world %>% 
  filter(continent == "Africa") %>% 
  select(ojs_total_active = total_active, ojs_total = total, ojs_v3_active, ojs_v3, ojs_v2_active, ojs_v2) %>% 
  summarize_all(sum, na.rm = TRUE)
```


```{r, out.width="100%"}
plot <-
  shapefile %>% 
  janitor::clean_names() %>%
  rename(country = name) %>%
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country),
    country = if_else(country == "Viet Nam", "Vietnam", country),
    country = if_else(str_detect(country, "Iran"), "Iran", country),
    country = if_else(str_detect(country, "Korea, Republic of"), "South Korea", country),
    country = if_else(str_detect(country, "Korea, Democratic People's Republic of"), "North Korea", country),
    country = if_else(str_detect(country, "Surinam"), "Surinam", country)
  ) %>%
  filter(region == 2) %>% 
  left_join(df_world, by = "country") %>% 
  mutate(
    total = replace_na(total, 0),
    total_active = replace_na(total_active, 0),
    ojs_v2 = replace_na(ojs_v2, 0),
    ojs_v2_active = replace_na(ojs_v2_active, 0),
    ojs_v3 = replace_na(ojs_v3, 0),
    ojs_v3_active = replace_na(ojs_v3_active, 0),
    subtext1 = str_c("Journals: ", total_active, " active (", total, " present)"),
    subtext2 = str_c("V3: ", ojs_v3_active, " active (", ojs_v3, " present)"),
    subtext3 = str_c("V2: ", ojs_v2_active, " active (", ojs_v2, " present)"),
    hover_text = str_c(country, subtext1, subtext2, subtext3, sep = "\n"),
    total_active = pmin(total_active, 20)
  ) %>%
  ggplot() +
  geom_sf(aes(fill = total_active, text = hover_text), size = 0.3, show.legend = FALSE) +
  scale_fill_gradientn(
    breaks = seq(0, 5, 20),
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd"),
    labels = labels
  ) +
  theme_minimal()

ggplotly(plot, tooltip = "hover_text") %>% 
  layout(xaxis = list(autorange = TRUE), yaxis = list(autorange = TRUE))
```


```{r}
df_world %>% 
  filter(continent == "Africa") %>% 
  arrange(-total_active) %>% 
  select(Country = country, Active = total_active, Present = total, `V3 active` = ojs_v3_active, `V3 present` = ojs_v3, `V2 active` = ojs_v2_active, `V2 present` = ojs_v2) %>% 
  DT::datatable()
```

#### OJS Version 2 installation URLs in Africa by number of active and present journals

```{r}
df_world_install %>% 
  filter(continent == "Africa", ojs_v2 > 0) %>% 
  arrange(country, desc(ojs_v2_active)) %>% 
  mutate(domain = str_c('<a href="http://', domain, '" target="_blank">', domain, '</a>')) %>% 
  select(Country = country, `V2 installation URL` = domain, `V2 active` = ojs_v2_active, `V2 present` = ojs_v2) %>% 
  DT::datatable(escape = F)
```

---

### Latin American Use of OJS by Version, 2017-19
**Active journals using OJS (5 records/year): 2017, 2018 or 2019**

Total count: 2,691 active (4,826 present)

OJS 3: 1,770 active (3,544 present)

OJS 2: 921 active (1,282 present)

```{r, eval = F}
# totals
df_world %>%
  filter(continent == "Americas", !(country %in% c("Canada", "United States"))) %>%
  select(ojs_total_active = total_active, ojs_total = total, ojs_v3_active, ojs_v3, ojs_v2_active, ojs_v2) %>% 
  summarize_all(sum, na.rm = TRUE)
```


```{r, out.width="100%"}
plot <-
  shapefile %>% 
  janitor::clean_names() %>%
  rename(country = name) %>%
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country),
    country = if_else(country == "Viet Nam", "Vietnam", country),
    country = if_else(str_detect(country, "Iran"), "Iran", country),
    country = if_else(str_detect(country, "Korea, Republic of"), "South Korea", country),
    country = if_else(str_detect(country, "Korea, Democratic People's Republic of"), "North Korea", country),
    country = if_else(str_detect(country, "Surinam"), "Surinam", country),
  ) %>%
  filter(region == 19, subregion != 21) %>%  
  left_join(df_world, by = "country") %>% 
  mutate(
    total = replace_na(total, 0),
    total_active = replace_na(total_active, 0),
    ojs_v2 = replace_na(ojs_v2, 0),
    ojs_v2_active = replace_na(ojs_v2_active, 0),
    ojs_v3 = replace_na(ojs_v3, 0),
    ojs_v3_active = replace_na(ojs_v3_active, 0),
    subtext1 = str_c("Journals: ", total_active, " active (", total, " present)"),
    subtext2 = str_c("V3: ", ojs_v3_active, " active (", ojs_v3, " present)"),
    subtext3 = str_c("V2: ", ojs_v2_active, " active (", ojs_v2, " present)"),
    hover_text = str_c(country, subtext1, subtext2, subtext3, sep = "\n"),
    total_active = pmin(total_active, 400)
  ) %>%
  ggplot() +
  geom_sf(aes(fill = total_active, text = hover_text), size = 0.3, show.legend = FALSE) +
  scale_fill_gradientn(
    breaks = seq(0, 400, 200),
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd"),
    labels = labels
  ) +
  theme_minimal()

ggplotly(plot, tooltip = "hover_text") %>% 
  layout(xaxis = list(autorange = TRUE), yaxis = list(autorange = TRUE))
```


```{r}
df_world %>% 
  filter(continent == "Americas", !(country %in% c("Canada", "United States"))) %>%
  arrange(-total_active) %>% 
  select(Country = country, Active = total_active, Present = total, `V3 active` = ojs_v3_active, `V3 present` = ojs_v3, `V2 active` = ojs_v2_active, `V2 present` = ojs_v2) %>% 
  DT::datatable()
```

#### OJS Version 2 installation URLs in Latin America by number of active and present journals

```{r}
df_world_install %>% 
  filter(continent == "Americas", !(country %in% c("Canada", "United States")), ojs_v2 > 0) %>%
  arrange(country, desc(ojs_v2_active)) %>% 
  mutate(domain = str_c('<a href="http://', domain, '" target="_blank">', domain, '</a>')) %>% 
  select(Country = country, `V2 installation URL` = domain, `V2 active` = ojs_v2_active, `V2 present` = ojs_v2) %>% 
  DT::datatable(escape = F)
```


<br/>

---

<small><b>1</b> The `hover` in interactive maps works along country borders instead of within country regions. When 2 countries share a border, the `hover` shows the country with more active journals.</small>

