---
title: "Global Use of OJS"
subtitle: "Active journals (at least 10 records since the start of 2019) using OJS"
date: "Updated: `r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 4
---

---

### Global

```{r setup, include=FALSE}
# knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.retina = 4)
```


```{r message=FALSE, warning=FALSE}
# Libraries
pacman::p_load(tidyverse, countrycode, sf, state, htmltools, htmlwidgets, urltools, janitor, DT, RColorBrewer, plotly, readxl)
tld <- read_csv(here::here("data/tld-country.csv"))
tld_from_ip <- read_csv(here::here("data/tld_from_ip.csv"))
shapefile <- read_sf(here::here("data/TM_WORLD_BORDERS_SIMPL-0.3.shp"))

# merging morocco and western sahara
# shapefile <-
#   shapefile %>% 
#   clean_names() %>% 
#   mutate(
#     name = if_else(name == "Western Sahara", "Morocco", name)
#   ) %>%
#   arrange(name) %>% 
#   group_by(name) %>% 
#   summarize(
#     geometry = st_union(geometry),
#     lat = first(lat),
#     lon = first(lon),
#     region = first(region),
#     subregion = first(subregion)
#   ) %>% 
#   st_cast("MULTIPOLYGON")
```



```{r}
# Data (May 17, 2021)
df <- read_csv(here::here("data/jonas/report-latest.csv"))

canada.states <- 
  c("Alberta", "British Columbia", "Labrador", "Manitoba", "New Brunswick", "Newfoundland", "Nova Scotia", "Nunavut", "North West Terr.", "Ontario", "Prince Edward Is.", "Québec (Province)", "Saskatchewan", "Yukon")

# correcting some oai urls
df <- 
  df %>% 
  mutate(oai_url = if_else(str_detect(oai_url, "^//"), str_c("http:", oai_url), oai_url))


# getting domain and tld
df <-  
  bind_cols(
    df,
    df %>% pull(oai_url) %>% domain() %>% tld_extract()
  ) %>% 
  mutate(country_consolidated = str_to_lower(country_consolidated) %>% str_trim()) %>% 
  left_join(tld, by = c("country_consolidated" = "tld"))

# Cleaning countries + Mapping countries to continents
df <-
  df %>% 
  mutate(
    country = country_clean,
    ojs_v2 = str_detect(version, "^2"),
    ojs_v3 = str_detect(version, "^3"),
    version_clean = case_when(
      ojs_v2 ~ "Version 2",
      ojs_v3 ~ "Version 3",
      TRUE ~ "Other"
    )
  ) %>% 
  mutate(
    country = if_else(country == "Washington (State)", "United States", country),
    country = if_else(str_detect(country, "United States|New York|District of Columbia"), "United States", country),
    country = if_else(country %in% state.name, "United States", country),
    country = if_else(country %in% canada.states, "Canada", country),
    country = if_else(str_detect(country, "China"), "China", country),
    country = if_else(str_detect(country, "Armenia"), "Armenia", country),
    country = if_else(str_detect(country, "Georgia"), "Georgia", country),
    country = if_else(str_detect(country, "Australia|New South Wales|Queensland|Victoria"), "Australia", country),
    country = if_else(str_detect(country, "England|British"), "United Kingdom", country),
    country = if_else(str_detect(country, "Russia|Soviet Union"), "Russia", country),
    country = if_else(str_detect(country, "Palestine"), "Palestine", country),
    country = if_else(country == "Korea (South)", "South Korea", country)
  ) %>% 
  select(-country_clean)

continents <-
  df %>%
  pull(country) %>% 
  countrycode(origin = "country.name", destination = "continent")

df <- df %>% bind_cols(continents)

# rename last column to `continent`
names(df)[length(names(df))] <- "continent"

df <-
  df %>% 
  filter(total_record_count > 0) %>% 
  mutate(
    active = ((record_count_2019 + record_count_2020 + record_count_2021) >= 10),
    active2019 = (record_count_2019 >= 5),
    active2020 = (record_count_2020 >= 5),
    active2021 = (record_count_2021 >= 5)
  ) %>%
  distinct(oai_url, repository_name, set_spec, .keep_all = T)
```


```{r}
# michaels list (after figuring out alive domains)
df_domains <- df %>% mutate(domain = str_replace(domain, "^www.", "")) %>% distinct(domain) %>% pull(domain)

df_pkp <- read_csv(here::here("data/michael_pkp_list_with_alive_flag.csv")) %>% clean_names() %>% remove_empty()

df_pkp <-  
  bind_cols(
    df_pkp,
    df_pkp %>% pull(url) %>% domain() %>% tld_extract()
  ) %>% 
  mutate(
    # source = source %>% str_to_upper() %>% str_trim(),
    domain = str_replace(domain, "^www.", ""),
    domain_in_beacon = (domain %in% df_domains)
  ) %>% 
  select(-tld) %>% 
  arrange(source, desc(alive), domain_in_beacon) %>% 
  rename(url_alive = alive, journal_path = url, journal_name = source)


# for sending back to michael
df_pkp %>% writexl::write_xlsx(here::here("data/michael_pkp_list_v2.xlsx"))
  
  


### STATS ###  
# Domain: 225/332 (67%) domains are not in the beacon
df_pkp %>% 
  count(domain) %>% 
  anti_join(
    df %>% mutate(domain = str_replace(domain, "^www.", "")) %>% distinct(domain),
    by = "domain"
  ) %>% 
  arrange(-n)


# # Name: 555/821 (67%) journals are not in the beacon
# df_pkp %>%
#   count(journal_name) %>%
#   anti_join(
#     df %>% mutate(context_name = context_name %>% str_to_upper() %>% str_trim()) %>% distinct(context_name),
#     by = c("journal_name" = "context_name")
#   ) %>%
#   arrange(-n) %>%
#   drop_na()

df_pkp %>% glimpse()
```



```{r}
# filtering top 100 active journals by record count
df %>%
  filter(active) %>% 
  arrange(desc(total_record_count)) %>% 
  select(context_name, total_record_count, domain) %>% 
  head(100) %>%
  mutate(domain = str_c('<a href="http://', domain, '" target="_blank">', domain, '</a>')) %>% 
  DT::datatable(escape = F)
```



```{r, eval=FALSE}
df %>% summarize_all(~ sum(is.na(.)))
df %>% glimpse()

df %>% drop_na(country) %>% count(active)

df %>% drop_na(country) %>% count(active2019)
df %>% drop_na(country) %>% count(active2020)
df %>% drop_na(country) %>% count(active2021)

# 450/13685 (3.3%) domain urls unresponsive
df %>% count(unresponsive)
df %>% count(domain)

df %>% filter(unresponsive == 1) %>% count(oai_url)

# df %>%
#   drop_na(country) %>%
#   filter(active) %>%
#   relocate(country, set_spec, context_name, repository_name, domain, issn, total_record_count, active) %>%
#   arrange(country, repository_name, set_spec, context_name, domain, issn, total_record_count) %>%
#   select(-(record_count_1300:record_count_1979)) %>% 
#   #filter(country == "Ecuador") %>% write_csv("ecuador_ojs_active_09.08.2021.csv")
#   write_csv("beacon_active_deduped_with_omp_ops_06.02.2021.csv")
```



```{r}
# creating grouped dfs
# df_world <-
#   df %>%
#   tabyl(country, active) %>%
#   as_tibble() %>%
#   drop_na(country) %>%
#   rename(inactive = `FALSE`, active = `TRUE`) %>%
#   mutate(
#     total = inactive + active,
#     perc_active = ((active/total) * 100) %>% round(digits = 2)
#   ) %>%
#   arrange(-total)
# 
# df_world
# 
# df_world %>% summarize(
#   total = sum(total, na.rm = T),
#   active = sum(active, na.rm = T),
#   inactive = sum(inactive, na.rm = T),
# )


# global df
df_world <-
  df %>%
  filter(active) %>% 
  drop_na(country) %>%
  group_by(country, continent) %>%
  summarize(
    total = sum(active, na.rm = T),
    ojs_v2 = sum(ojs_v2, na.rm = T),
    ojs_v3 = sum(ojs_v3, na.rm = T)
  ) %>%
  ungroup() %>%
  transmute(
    country,
    continent,
    ojs_v2 = replace_na(ojs_v2, 0),
    ojs_v3 = replace_na(ojs_v3, 0),
    total = replace_na(total, 0)
  )

 
active_sum <- df_world %>% summarise(active_sum = sum(total, na.rm = TRUE)) %>% pull(active_sum)
v2_sum <- df_world %>% summarise(v2_sum = sum(ojs_v2, na.rm = TRUE)) %>% pull(v2_sum)
v3_sum <- df_world %>% summarise(v3_sum = sum(ojs_v3, na.rm = TRUE)) %>% pull(v3_sum)
```

Total OJS count: `r toString(active_sum)` active journals<sup>1</sup>

OJS v3 count: `r toString(v3_sum)` active journals

OJS v2 count: `r toString(v2_sum)` active journals


```{r}
# creating installation df
df_world_install <-
  df %>%
  filter(active) %>% 
  drop_na(country) %>%   
  group_by(country, continent, domain) %>% 
  summarize(ojs_v2 = sum(ojs_v2, na.rm = T)) %>% 
  ungroup() %>% 
  filter(ojs_v2 > 0)
```

---

```{r, out.width="100%"}
plot <-
  shapefile %>% 
  clean_names() %>%
  rename(country = name) %>%
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country),
    country = if_else(country == "Viet Nam", "Vietnam", country),
    country = if_else(str_detect(country, "Iran"), "Iran", country),
    country = if_else(str_detect(country, "Korea, Republic of"), "South Korea", country),
    country = if_else(str_detect(country, "Korea, Democratic People's Republic of"), "North Korea", country),
    country = if_else(str_detect(country, "Surinam"), "Surinam", country)
  ) %>%
  left_join(df_world, by = "country") %>% 
  filter(country != "Antarctica") %>% 
  mutate(
    total = replace_na(total, 0),
    ojs_v2 = replace_na(ojs_v2, 0),
    ojs_v3 = replace_na(ojs_v3, 0),
    subtext1 = str_c("Journals: ", total),
    subtext2 = str_c("V3: ", ojs_v3),
    subtext3 = str_c("V2: ", ojs_v2),
    hover_text = str_c(country, subtext1, subtext2, subtext3, sep = "\n"),
    total = pmin(total, 500)
  ) %>%
  ggplot() +
  geom_sf(aes(fill = total, text = hover_text), size = 0.3, show.legend = FALSE) +
  scale_fill_gradientn(
    breaks = seq(0, 500, 250),
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd")
  ) +
  theme_minimal()

ggplotly(plot, tooltip = "hover_text") %>% 
  layout(xaxis = list(autorange = TRUE), yaxis = list(autorange = TRUE))
```

```{r}
df_world %>% 
  arrange(-total) %>%
  select(country, total, ojs_v3, ojs_v2) %>% 
  DT::datatable()
```


<br/>



### Africa


```{r}
active_sum <- df_world %>% filter(continent == "Africa") %>% summarise(active_sum = sum(total, na.rm = TRUE)) %>% pull(active_sum)
v2_sum <- df_world %>% filter(continent == "Africa") %>% summarise(v2_sum = sum(ojs_v2, na.rm = TRUE)) %>% pull(v2_sum)
v3_sum <- df_world %>% filter(continent == "Africa") %>% summarise(v3_sum = sum(ojs_v3, na.rm = TRUE)) %>% pull(v3_sum)
```

---

Total OJS count: `r toString(active_sum)` active journals

OJS v3 count: `r toString(v3_sum)` active journals

OJS v2 count: `r toString(v2_sum)` active journals

---

```{r}
plot <-
  shapefile %>% 
  janitor::clean_names() %>%
  rename(country = name) %>%
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country),
    country = if_else(country == "Viet Nam", "Vietnam", country),
    country = if_else(str_detect(country, "Iran"), "Iran", country),
    country = if_else(str_detect(country, "Korea, Republic of"), "South Korea", country),
    country = if_else(str_detect(country, "Korea, Democratic People's Republic of"), "North Korea", country),
    country = if_else(str_detect(country, "Surinam"), "Surinam", country)
  ) %>%
  filter(region == 2) %>% 
  left_join(df_world, by = "country") %>% 
  mutate(
    total = replace_na(total, 0),
    ojs_v2 = replace_na(ojs_v2, 0),
    ojs_v3 = replace_na(ojs_v3, 0),
    subtext1 = str_c("Journals: ", total),
    subtext2 = str_c("V3: ", ojs_v3),
    subtext3 = str_c("V2: ", ojs_v2),
    hover_text = str_c(country, subtext1, subtext2, subtext3, sep = "\n"),
    total = pmin(total, 30)
  ) %>%
  ggplot() +
  geom_sf(aes(fill = total, text = hover_text), size = 0.3, show.legend = FALSE) +
  scale_fill_gradientn(
    breaks = seq(0, 5, 20),
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd"),
    labels = labels
  ) +
  theme_minimal()

ggplotly(plot, tooltip = "hover_text") %>% 
  layout(xaxis = list(autorange = TRUE), yaxis = list(autorange = TRUE))
```

```{r}
df_world %>% 
  filter(continent == "Africa") %>% 
  arrange(-total) %>%
  select(country, total, ojs_v3, ojs_v2) %>% 
  DT::datatable()
```

#### Active OJS Version 2 installation URLs

```{r}
df_world_install %>% 
  filter(continent == "Africa") %>% 
  arrange(desc(ojs_v2)) %>% 
  mutate(domain = str_c('<a href="http://', domain, '" target="_blank">', domain, '</a>')) %>% 
  select(Country = country, `V2 installation URL` = domain, `V2 active journals` = ojs_v2) %>% 
  DT::datatable(escape = F)
```



<br/>



### Latin America


```{r}
active_sum <- df_world %>% filter(continent == "Americas", !(country %in% c("Canada", "United States"))) %>% summarise(active_sum = sum(total, na.rm = TRUE)) %>% pull(active_sum)
v2_sum <- df_world %>% filter(continent == "Americas", !(country %in% c("Canada", "United States"))) %>% summarise(v2_sum = sum(ojs_v2, na.rm = TRUE)) %>% pull(v2_sum)
v3_sum <- df_world %>% filter(continent == "Americas", !(country %in% c("Canada", "United States"))) %>% summarise(v3_sum = sum(ojs_v3, na.rm = TRUE)) %>% pull(v3_sum)
```

---

Total OJS count: `r toString(active_sum)` active journals

OJS v3 count: `r toString(v3_sum)` active journals

OJS v2 count: `r toString(v2_sum)` active journals

---

```{r}
plot <-
  shapefile %>% 
  janitor::clean_names() %>%
  rename(country = name) %>%
  mutate(
    country = if_else(country == "Libyan Arab Jamahiriya", "Libya", country),
    country = if_else(country == "United Republic of Tanzania", "Tanzania", country),
    country = if_else(country == "Cote d'Ivoire", "Côte d'Ivoire", country),
    country = if_else(country == "Congo", "Republic of the Congo", country),
    country = if_else(country == "Viet Nam", "Vietnam", country),
    country = if_else(str_detect(country, "Iran"), "Iran", country),
    country = if_else(str_detect(country, "Korea, Republic of"), "South Korea", country),
    country = if_else(str_detect(country, "Korea, Democratic People's Republic of"), "North Korea", country),
    country = if_else(str_detect(country, "Surinam"), "Surinam", country)
  ) %>%
  filter(region == 19, subregion != 21) %>%  
  left_join(df_world, by = "country") %>% 
  mutate(
    total = replace_na(total, 0),
    ojs_v2 = replace_na(ojs_v2, 0),
    ojs_v3 = replace_na(ojs_v3, 0),
    subtext1 = str_c("Journals: ", total),
    subtext2 = str_c("V3: ", ojs_v3),
    subtext3 = str_c("V2: ", ojs_v2),
    hover_text = str_c(country, subtext1, subtext2, subtext3, sep = "\n"),
    total = pmin(total, 900)
  ) %>%
  ggplot() +
  geom_sf(aes(fill = total, text = hover_text), size = 0.3, show.legend = FALSE) +
  scale_fill_gradientn(
    breaks = seq(0, 5, 20),
    colors = RColorBrewer::brewer.pal(n = 9, name = "PuRd"),
    labels = labels
  ) +
  theme_minimal()

ggplotly(plot, tooltip = "hover_text") %>% 
  layout(xaxis = list(autorange = TRUE), yaxis = list(autorange = TRUE))
```

```{r}
df_world %>% 
  filter(continent == "Americas", !(country %in% c("Canada", "United States"))) %>%
  arrange(-total) %>%
  select(country, total, ojs_v3, ojs_v2) %>% 
  DT::datatable()
```

#### Active OJS Version 2 installation URLs

```{r}
df_world_install %>% 
  filter(continent == "Americas", !(country %in% c("Canada", "United States"))) %>%
  arrange(desc(ojs_v2)) %>% 
  mutate(domain = str_c('<a href="http://', domain, '" target="_blank">', domain, '</a>')) %>% 
  select(Country = country, `V2 installation URL` = domain, `V2 active journals` = ojs_v2) %>% 
  DT::datatable(escape = F)
```


<br/>

### Indonesia


```{r}
active_sum <- df_world %>% filter(country == "Indonesia") %>% summarise(active_sum = sum(total, na.rm = TRUE)) %>% pull(active_sum)
v2_sum <- df_world %>% filter(country == "Indonesia") %>% summarise(v2_sum = sum(ojs_v2, na.rm = TRUE)) %>% pull(v2_sum)
v3_sum <- df_world %>% filter(country == "Indonesia") %>% summarise(v3_sum = sum(ojs_v3, na.rm = TRUE)) %>% pull(v3_sum)
```

---

Total OJS count: `r toString(active_sum)` active journals

OJS v3 count: `r toString(v3_sum)` active journals

OJS v2 count: `r toString(v2_sum)` active journals

---

#### Active OJS Version 2 installation URLs

```{r}
df_world_install %>% 
  filter(country == "Indonesia") %>% 
  arrange(desc(ojs_v2)) %>% 
  mutate(domain = str_c('<a href="http://', domain, '" target="_blank">', domain, '</a>')) %>% 
  select(Country = country, `V2 installation URL` = domain, `V2 active journals` = ojs_v2) %>% 
  DT::datatable(escape = F)
```



```{r, eval=F}
# detective work for kevin
df_doaj <- 
  read_excel(here::here("data/kevin/kevin_doaj.xlsx")) %>% clean_names() %>% 
  remove_empty()

df_doaj <-
  bind_cols(
    df_doaj,
    df_doaj %>% pull(journal_url) %>% domain() %>% tld_extract()
  ) %>%
  mutate(
    platform = platform_host_or_aggregator %>% str_trim() %>% str_to_upper(),
    journal_title = journal_title %>% str_trim() %>% str_to_upper(),
    publisher = publisher %>% str_trim() %>% str_to_upper(),
    country = country_of_publisher %>% str_trim(),
    issn = journal_eissn_online_version %>% str_trim(),
    ojs = str_detect(platform, "OJS|NEPJOL|AJOL|SEER|OPEN JOURNAL SYSTEM")
  )

# question 1
df_doaj %>% 
  filter(ojs) %>% 
  anti_join(df, by = "issn") %>% 
  # anti_join(df, by = "domain") %>%
  # anti_join(df, by = c("journal_title" = "set_spec")) %>%
  # anti_join(df, by = c("publisher" = "repository_name")) %>%
  arrange(country, publisher, journal_title) %>% 
  relocate(country, issn, ojs, publisher, journal_title) %>% 
  #writexl::write_xlsx(here::here("doaj_journals_not_in_beacon_07.16.2021.xlsx"))
  count(country) %>% arrange(-n)

df_doaj %>% 
  filter(ojs) %>% 
  anti_join(df, by = "issn") %>% 
  anti_join(df, by = "domain") %>% 
  anti_join(df, by = c("journal_title" = "set_spec")) %>% 
  anti_join(df, by = c("publisher" = "repository_name")) %>% 
  arrange(country, publisher, journal_title) %>% 
  relocate(country, issn, ojs, publisher, journal_title) %>% 
  summarise_all(~ mean(is.na(.)))

# question 2
# df_doaj %>%
#   filter((!ojs | is.na(ojs)) & !is.na(issn)) %>%
#   inner_join(df, by = "issn")
# 
# df_doaj %>%
#   filter((!ojs | is.na(ojs)) & !is.na(domain)) %>%
#   inner_join(df, by = "domain")
# checks

df_doaj %>% 
  filter(ojs) %>% 
  anti_join(df, by = "issn") %>% 
  anti_join(df, by = "domain") %>% 
  anti_join(df, by = c("journal_title" = "set_spec")) %>% 
  anti_join(df, by = c("publisher" = "repository_name")) %>% 
  arrange(country, publisher, journal_title) %>% 
  relocate(country, publisher, journal_title) %>% 
  filter(str_detect(country, "Finland")) %>% 
  distinct(domain)

df_doaj %>% 
  filter(ojs) %>% 
  anti_join(df, by = "issn") %>% 
  anti_join(df, by = "domain") %>% 
  anti_join(df, by = c("journal_title" = "set_spec")) %>% 
  anti_join(df, by = c("publisher" = "repository_name")) %>% 
  arrange(country, publisher, journal_title) %>% 
  relocate(country, publisher, journal_title) %>%
  distinct(domain)
```



```{r, eval=F}
# predatory matching

pred_list <- 
  read_csv("/home/saurabh/Everything/GitHub/beall-live/data/df_weekly.csv") %>% 
  clean_names() %>% 
  remove_empty()

pred_list <-
  bind_cols(
    pred_list,
    pred_list %>% pull(url) %>% domain() %>% tld_extract()
  ) %>% 
  relocate(domain) %>% 
  mutate(
    domain = str_replace(domain, "^www.", "")
  ) %>% 
  distinct(domain, .keep_all = T)

pred_list

df_pred <- 
  df %>%
  mutate(
    domain = str_replace(domain, "^www.", "")
  ) %>%
  inner_join(pred_list, by = "domain") %>%
  relocate(domain)


# 55 out of 1329 publisher domains (4% domains are in the beacon)
# 498 journals (252 active, 246 inactive) [0.9% active and 1.6% inactive OJS journals]
# US and India

df_pred %>% count(domain) %>% arrange(-n)

df_pred %>% count(active)

df_pred %>% count(country) %>% arrange(-n)

242/(41202-26689)
```




<br/>

---

<small><b>1</b> The `hover` in the interactive map works along country borders instead of within country regions. When two countries share a border, the `hover` shows the country with more active journals.</small>
