---
title: "Assessing OJS overlaps with scientometric databases"
date: "Updated: `r format(Sys.Date(), format='%B %d, %Y')`"
output:
  github_document:
    toc: true
    toc_depth: 6
    number_sections: no
---

---

```{r setup, include=FALSE}
# knitr options
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```


```{r message=FALSE, warning=FALSE}
# Libraries
pacman::p_load(tidyverse, countrycode, sf, state, htmltools, htmlwidgets, urltools, janitor, DT, RColorBrewer, plotly, readxl)

# raw beacon data
df <- read_csv(here::here("data/beacon-public.csv")) 

# ancillary data and vectors for cleaning
iso_to_name <- read_csv(here::here("data/country-iso3166-to-name.csv"))

canada.states <- 
  c(
    "Alberta", "British Columbia", "Labrador", "Manitoba", "New Brunswick", "Newfoundland", "Nova Scotia", "Nunavut", "North West Terr.", "Ontario", "Prince Edward Is.", "Québec (Province)", "Saskatchewan", "Yukon"
  )
```


## Cleaning raw beacon data

```{r}
# Cleaning oai urls
df <- 
  df %>% 
  mutate(oai_url = if_else(str_detect(oai_url, "^//"), str_c("http:", oai_url), oai_url))


# Getting domain, tld, and merging in country names
df <-  
  bind_cols(
    df,
    df %>% pull(oai_url) %>% domain() %>% tld_extract()
  ) %>% 
  mutate(country_consolidated = str_to_lower(country_consolidated) %>% str_trim()) %>% 
  left_join(iso_to_name, by = c("country_consolidated" = "tld"))


# Cleaning country names
df <-
  df %>% 
  mutate(
    country = country_clean,
    country = if_else(country == "Washington (State)", "United States", country),
    country = if_else(str_detect(country, "United States|New York|District of Columbia"), "United States", country),
    country = if_else(country %in% state.name, "United States", country),
    country = if_else(country %in% canada.states, "Canada", country),
    country = if_else(str_detect(country, "China"), "China", country),
    country = if_else(str_detect(country, "Armenia"), "Armenia", country),
    country = if_else(str_detect(country, "Georgia"), "Georgia", country),
    country = if_else(str_detect(country, "Australia|New South Wales|Queensland|Victoria"), "Australia", country),
    country = if_else(str_detect(country, "England|British"), "United Kingdom", country),
    country = if_else(str_detect(country, "Russia|Soviet Union"), "Russia", country),
    country = if_else(str_detect(country, "Palestine"), "Palestine", country),
    country = if_else(country == "Korea (South)", "South Korea", country)
  ) %>% 
  select(-country_clean, -country_marc, -country_issn, -country_tld, -country_ip)


# Mapping countries to continents
continents <-
  df %>%
  pull(country) %>% 
  countrycode(origin = "country.name", destination = "continent")

df <- df %>% bind_cols(continents)

# Rename last column to `continent`
names(df)[length(names(df))] <- "continent"
```



```{r}
# Filter to active OJS journals
df <-
  df %>% 
  filter(application == "ojs", record_count_2020 >= 5) %>% 
  distinct(oai_url, repository_name, set_spec, .keep_all = T)
```

Total active journals using OJS (JUOJS):

```{r}
df %>% count()
```

Total articles published in active JUOJS:

```{r}
df %>% summarise(total = sum(record_count_2020, na.rm = T))
```

Average articles published in active JUOJS:

```{r}
df %>% summarise(total = mean(record_count_2020, na.rm = T))
```


Total distinct ISSNs:

```{r}
df %>% 
  mutate(
    issn = str_extract(issn, "[^\n]+") # correcting for multiple reported issns
  ) %>% 
  distinct(issn) %>% 
  drop_na(issn) %>% 
  count()
```

---

<br/><br/>

## Assessing overlaps

### Web of Science

Total overlap:

```{r, fig.retina=4}
df_wos <-
  read_table(here::here("data/overlaps/wos.txt"), na = c("NULL", "NA", "")) %>% 
  clean_names() %>% 
  remove_empty() %>% 
  filter(str_detect(issn, "^[0-9]{4}-[0-9]{3}[0-9xX]$")) %>% 
  distinct(issn) %>% 
  drop_na(issn)

# total overlap
df %>% 
  mutate(
    issn = str_extract(issn, "[^\n]+")
  ) %>%
  inner_join(df_wos, by = "issn") %>% 
  count()
```

Top 10 countries in overlap:

```{r}
# top 10 countries in overlap
df %>% 
  mutate(
    issn = str_extract(issn, "[^\n]+")
  ) %>%
  inner_join(df_wos, by = "issn") %>% 
  count(country) %>% 
  arrange(-n) %>% 
  head(10) %>% 
  mutate(country = fct_inorder(country) %>% fct_rev()) %>% 
  ggplot(aes(country, n)) +
  geom_col(fill = "#0072B2") +
  theme_classic() +
  theme(
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 18),
    axis.ticks = element_blank()
  ) +
  coord_flip() +
  labs(
    x = "Country", y = "Number of journals"
  )
```


### Scopus

Total overlap:

```{r}
# Scopus data
df_scopus <-
  read_excel(here::here("data/overlaps/scopus.xlsx")) %>%
  clean_names() %>% 
  remove_empty() %>%
  transmute(
    issn = str_replace(print_issn, "-", ""),
    e_issn = str_replace(e_issn, "-", "")
  ) %>%
  distinct() %>% 
  remove_empty()

# join A (issn to issn)
df_join_a <-
  df %>%
  drop_na(issn) %>% 
  transmute(
    country,
    issn = str_extract(issn, "[^\n]+"),
    issn = str_replace(issn, "-", "")
  ) %>%
  distinct(issn, .keep_all = T) %>% 
  inner_join(df_scopus %>% select(-e_issn), by = "issn")

# join B (issn to e-issn)
df_join_b <-
  df %>%
  drop_na(issn) %>% 
  transmute(
    country,
    issn = str_extract(issn, "[^\n]+"),
    issn = str_replace(issn, "-", "")
  ) %>%
  distinct(issn, .keep_all = T) %>% 
  inner_join(df_scopus %>% select(-issn), by = c("issn" = "e_issn"))

bind_rows(df_join_a, df_join_b) %>% 
  distinct() %>% 
  count()

# 1646/41957
# 1646/22809
```

Top 10 countries in overlap:

```{r}
bind_rows(df_join_a, df_join_b) %>% 
  distinct() %>%
  drop_na(country) %>% 
  count(country) %>% 
  arrange(-n) %>% 
  head(10) %>% 
  mutate(country = fct_inorder(country) %>% fct_rev()) %>% 
  ggplot(aes(country, n)) +
  geom_col(fill = "#0072B2") +
  theme_classic() +
  theme(
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 18),
    axis.ticks = element_blank()
  ) +
  coord_flip() +
  labs(
    x = "Country", y = "Number of journals"
  )
```

```{r, echo=F}
rm(df_join_a, df_join_b)
```

### Dimensions

Total overlap:

```{r}
# Dimensions data
df_dimensions <-
  read_excel(here::here("data/overlaps/dimensions.xlsx")) %>%
  clean_names() %>% 
  remove_empty() %>% 
  transmute(
    issn = str_replace(issn_print, "-", "") %>% na_if("NULL"),
    e_issn = str_replace(issn_e, "-", "") %>% na_if("NULL")
  ) %>%
  distinct() %>% 
  remove_empty()


# join A (issn to issn)
df_join_a <-
  df %>%
  drop_na(issn) %>% 
  transmute(
    country,
    issn = str_extract(issn, "[^\n]+"),
    issn = str_replace(issn, "-", "")
  ) %>%
  distinct(issn, .keep_all = T) %>% 
  inner_join(df_dimensions %>% select(-e_issn), by = "issn")

# join B (issn to e-issn)
df_join_b <-
  df %>%
  drop_na(issn) %>% 
  transmute(
    country,
    issn = str_extract(issn, "[^\n]+"),
    issn = str_replace(issn, "-", "")
  ) %>%
  distinct(issn, .keep_all = T) %>% 
  inner_join(df_dimensions %>% select(-issn), by = c("issn" = "e_issn"))

bind_rows(df_join_a, df_join_b) %>% 
  distinct() %>% 
  count()

#12435/22809
#12435/72990
```

Top 10 countries in overlap:

```{r}
bind_rows(df_join_a, df_join_b) %>% 
  distinct() %>%
  drop_na(country) %>% 
  count(country) %>% 
  arrange(-n) %>% 
  head(10) %>% 
  mutate(country = fct_inorder(country) %>% fct_rev()) %>% 
  ggplot(aes(country, n)) +
  geom_col(fill = "#0072B2") +
  theme_classic() +
  theme(
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 18),
    axis.ticks = element_blank()
  ) +
  coord_flip() +
  labs(
    x = "Country", y = "Number of journals"
  )
```


```{r, echo=F}
rm(df_join_a, df_join_b)
```


### EBSCO Host

Total Overlap:

```{r}
# EBSCO Host
df_ebsco <-
  read_excel(here::here("data/overlaps/ebscohost.xls")) %>%
  clean_names() %>% 
  remove_empty() %>% 
  distinct(issn) %>% 
  drop_na(issn)

df %>% 
  drop_na(issn) %>%
  transmute(
    country,
    issn = str_extract(issn, "[^\n]+")
  ) %>%
  inner_join(df_ebsco, by = "issn") %>% 
  count()
```

Top 10 countries in overlap:

```{r}
df %>% 
  drop_na(issn) %>%
  transmute(
    country,
    issn = str_extract(issn, "[^\n]+")
  ) %>%
  inner_join(df_ebsco, by = "issn") %>%
  drop_na(country) %>% 
  count(country) %>% 
  arrange(-n) %>% 
  head(10) %>% 
  mutate(country = fct_inorder(country) %>% fct_rev()) %>% 
  ggplot(aes(country, n)) +
  geom_col(fill = "#0072B2") +
  coord_flip() +
  theme_classic() +
  theme(
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 10),
    axis.ticks = element_blank()
  ) +
  labs(
    x = "Country", y = "Number of journals"
  )
```

### Google Scholar

```{r, eval=F, echo=F}
# Extract URLs for gscholar script implemented in python

# df %>%
#   separate(oai_url, c("url1", "url2"), "\n") %>% 
#   remove_empty() %>% 
#   rename(oai_url = url1) %>% 
#   filter(!str_detect(oai_url, "\\?page=")) %>% 
#   transmute(
#     country, total_record_count, context_name,
#     url = str_replace(oai_url, "index/oai", set_spec),
#     url = str_replace(url, "^https://", ""),
#     url = str_replace(url, "^http://", ""),
#     url = str_replace(url, "^www108.", ""),
#     url = str_replace(url, "^www5.", ""),
#     url = str_replace(url, "^www3.", ""),
#     url = str_replace(url, "^www2.", ""),
#     url = str_replace(url, "^www.", ""),
#   ) %>%
#   bind_rows(
#     df %>%
#       separate(oai_url, c("url1", "url2"), "\n") %>% 
#       remove_empty() %>% 
#       rename(oai_url = url1) %>% 
#       filter(str_detect(oai_url, "\\?page=")) %>% 
#       transmute(
#         country, total_record_count, context_name,
#         url = str_replace(oai_url, "oai$", set_spec),
#         url = str_replace(url, "^https://", ""),
#         url = str_replace(url, "^http://", ""),
#         url = str_replace(url, "^www108.", ""),
#         url = str_replace(url, "^www5.", ""),
#         url = str_replace(url, "^www3.", ""),
#         url = str_replace(url, "^www2.", ""),
#         url = str_replace(url, "^www.", ""),
#       ), .
#   ) %>% 
#   write_csv(here::here("data/gscholar_urls.csv"))
```


```{r, fig.retina=4}
# Read in python processed google scholar URLs
## first iteration using journal URLs ##

df_gscholar <- 
  read_csv(here::here("scripts/gscholar_urls_mapped.csv")) %>% 
  select(-result_json) %>% 
  mutate(n_results = parse_integer(n_results))

df_gscholar <-
  df %>%
  separate(oai_url, c("url1", "url2"), "\n") %>% 
  remove_empty() %>% 
  rename(oai_url = url1) %>% 
  filter(!str_detect(oai_url, "\\?page=")) %>% 
  transmute(
    country, total_record_count, context_name,
    url = str_replace(oai_url, "index/oai", set_spec),
    url = str_replace(url, "^https://", ""),
    url = str_replace(url, "^http://", ""),
    url = str_replace(url, "^www108.", ""),
    url = str_replace(url, "^www5.", ""),
    url = str_replace(url, "^www3.", ""),
    url = str_replace(url, "^www2.", ""),
    url = str_replace(url, "^www.", ""),
  ) %>%
  bind_rows(
    df %>%
      separate(oai_url, c("url1", "url2"), "\n") %>% 
      remove_empty() %>% 
      rename(oai_url = url1) %>% 
      filter(str_detect(oai_url, "\\?page=")) %>% 
      transmute(
        country, total_record_count, context_name,
        url = str_replace(oai_url, "oai$", set_spec),
        url = str_replace(url, "^https://", ""),
        url = str_replace(url, "^http://", ""),
        url = str_replace(url, "^www108.", ""),
        url = str_replace(url, "^www5.", ""),
        url = str_replace(url, "^www3.", ""),
        url = str_replace(url, "^www2.", ""),
        url = str_replace(url, "^www.", ""),
      ), .
  ) %>% 
  distinct() %>% 
  inner_join(df_gscholar, by = "url")


# bind_cols(
#     df_gscholar,
#     df_gscholar %>% pull(url) %>% domain() %>% tld_extract()
#   ) %>%
#   left_join(read_csv(here::here("scripts/gscholar_citations.csv")), by = "url") %>% 
#   group_by(domain) %>% 
#   summarise(
#     n_results = sum(n_results, na.rm = T),
#     n_citations = sum(n_citations, na.rm = T)
#   ) %>% 
#   filter(n_results > 0) %>% 
#   select(-n_results) %>% 
#   write_csv(here::here("data/scholar_present_domains_set1.csv"))
```


Total overlap:

```{r}
# loading all domains
domains_in_scholar <-
  bind_rows(
    read_csv(here::here("data/scholar_present_domains_set1.csv")),
    read_csv(here::here("data/scholar_present_domains_set2.csv")),
  ) %>% 
  distinct()

# total overlap
bind_cols(
    df_gscholar,
    df_gscholar %>% pull(url) %>% domain() %>% tld_extract()
  ) %>% 
  inner_join(domains_in_scholar, by = "domain") %>%
  count()

#22679/25671

#domains_in_scholar %>% summary()
#domains_in_scholar %>% filter(n_citations < 1)
#552/8548
```



Top 10 countries in overlap:

```{r}
# top 10 countries in overlap
bind_cols(
    df_gscholar,
    df_gscholar %>% pull(url) %>% domain() %>% tld_extract()
  ) %>% 
  inner_join(domains_in_scholar, by = "domain") %>% 
  count(country) %>% 
  arrange(-n) %>% 
  mutate(country = fct_inorder(country) %>% fct_rev()) %>% 
  head(10) %>% 
  ggplot(aes(country, n)) +
  geom_col(fill = "#0072B2") +
  scale_y_continuous(breaks = scales::breaks_width(1000)) +
  theme_classic() +
  theme(
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 10),
    axis.ticks = element_blank()
  ) +
  coord_flip() +
  labs(x = "Country", y = "Total journals")
```

Number of citations on first Scholar page:

```{r scholar-citations, fig.retina=4}
# number of citations on first gscholar page
domains_in_scholar %>%
  mutate(n_citations = pmin(n_citations, 500)) %>% 
  ggplot(aes(n_citations)) +
  geom_histogram(binwidth = 20, fill = "#0072B2") +
  scale_x_continuous(labels = c("0", "100", "200", "300", "400", "500+")) +
  hrbrthemes::theme_ipsum() +
  labs(
    x = "Total citations on first page",
    y = "Number of journal domains"
  ) +
  theme_classic() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    axis.ticks = element_blank()
  )

# ggsave("scholar_citations.png")
```

Journals with non-zero citations on first page:

```{r}
# alter threshold to see proportions as needed (e.g. 0, 1000, 10000)
threshold <- 0

domains_in_scholar %>% arrange(-n_citations) %>% filter(n_citations > threshold) %>% count()
```

Summary of citations on first page:

```{r}
domains_in_scholar %>% summary()
```



### Latindex

Total Overlap:

```{r}
# Latindex
df_latindex <-
  read_excel(here::here("data/overlaps/latindex.xlsx")) %>%
  clean_names() %>% 
  remove_empty() %>% 
  select(issn, e_issn, online = en_linea) %>% 
  distinct()
  

# join A (issn to issn)
df_join_a <-
  df %>%
  drop_na(issn) %>% 
  transmute(
    country,
    issn = str_extract(issn, "[^\n]+")
  ) %>%
  distinct(issn, .keep_all = T) %>% 
  inner_join(df_latindex %>% select(-e_issn), by = "issn")

# join B (issn to e-issn)
df_join_b <-
  df %>%
  drop_na(issn) %>% 
  transmute(
    country,
    issn = str_extract(issn, "[^\n]+")
  ) %>%
  distinct(issn, .keep_all = T) %>% 
  inner_join(df_latindex %>% select(-issn), by = c("issn" = "e_issn"))

bind_rows(df_join_a, df_join_b) %>% 
  distinct() %>%
  arrange(country, issn, -online) %>% 
  distinct(country, issn) %>% 
  count()

# 4208/24486
# 4208/6319
```

Top 10 countries in overlap:

```{r}
bind_rows(df_join_a, df_join_b) %>% 
  distinct() %>%
  arrange(country, issn, -online) %>% 
  distinct(country, issn) %>%
  drop_na(country) %>% 
  count(country) %>% 
  arrange(-n) %>% 
  head(10) %>% 
  mutate(country = fct_inorder(country) %>% fct_rev()) %>% 
  ggplot(aes(country, n)) +
  geom_col(fill = "#0072B2") +
  coord_flip() +
  labs(
    x = "Country", y = "Number of journals"
  ) +
  theme_classic() +
  theme(
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 18),
    axis.ticks = element_blank()
  )
```


Latin American countries for JUOJS: 

```{r}
# Latin American countries for JUOJS
df_latam <- read_csv(here::here("data/latindex_countries.csv")) 

df %>% 
  inner_join(df_latam, by = "country") %>% 
  count()
```




