---
title: "Assessing OJS overlaps with scientometric databases"
author: "Public Knowledge Project"
date: "Updated: `r format(Sys.Date(), format='%B %d, %Y')`"
output:
  github_document:
    toc: true
    toc_depth: 6
    number_sections: no
---

---

```{r setup, include=FALSE}
# knitr options
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```


```{r message=FALSE, warning=FALSE}
# Libraries
pacman::p_load(tidyverse, countrycode, sf, state, htmltools, htmlwidgets, urltools, janitor, DT, RColorBrewer, plotly, readxl)

# raw beacon data
df <- read_csv(here::here("data/beacon-public.csv")) 

# ancillary data and vectors for cleaning
iso_to_name <- read_csv(here::here("data/country-iso3166-to-name.csv"))

canada.states <- 
  c(
    "Alberta", "British Columbia", "Labrador", "Manitoba", "New Brunswick", "Newfoundland", "Nova Scotia", "Nunavut", "North West Terr.", "Ontario", "Prince Edward Is.", "Québec (Province)", "Saskatchewan", "Yukon"
  )
```


## Cleaning raw beacon data

```{r}
# Cleaning oai urls
df <- 
  df %>% 
  mutate(oai_url = if_else(str_detect(oai_url, "^//"), str_c("http:", oai_url), oai_url))


# Getting domain, tld, and merging in country names
df <-  
  bind_cols(
    df,
    df %>% pull(oai_url) %>% domain() %>% tld_extract()
  ) %>% 
  mutate(country_consolidated = str_to_lower(country_consolidated) %>% str_trim()) %>% 
  left_join(iso_to_name, by = c("country_consolidated" = "tld"))


# Cleaning country names
df <-
  df %>% 
  mutate(
    country = country_clean,
    country = if_else(country == "Washington (State)", "United States", country),
    country = if_else(str_detect(country, "United States|New York|District of Columbia"), "United States", country),
    country = if_else(country %in% state.name, "United States", country),
    country = if_else(country %in% canada.states, "Canada", country),
    country = if_else(str_detect(country, "China"), "China", country),
    country = if_else(str_detect(country, "Armenia"), "Armenia", country),
    country = if_else(str_detect(country, "Georgia"), "Georgia", country),
    country = if_else(str_detect(country, "Australia|New South Wales|Queensland|Victoria"), "Australia", country),
    country = if_else(str_detect(country, "England|British"), "United Kingdom", country),
    country = if_else(str_detect(country, "Russia|Soviet Union"), "Russia", country),
    country = if_else(str_detect(country, "Palestine"), "Palestine", country),
    country = if_else(country == "Korea (South)", "South Korea", country)
  ) %>% 
  select(-country_clean, -country_marc, -country_issn, -country_tld, -country_ip)


# Mapping countries to continents
continents <-
  df %>%
  pull(country) %>% 
  countrycode(origin = "country.name", destination = "continent")

df <- df %>% bind_cols(continents)

# Rename last column to `continent`
names(df)[length(names(df))] <- "continent"

# Filter to active OJS journals
df <-
  df %>% 
  filter(application == "ojs", record_count_2020 >= 5) %>% 
  distinct(oai_url, repository_name, set_spec, .keep_all = T)
```

Total active OJS journals:

```{r}
df %>% count()
```


---

<br/><br/>

## Assessing overlaps

### Web of Science

Total overlap:

```{r, fig.retina=4}
df_wos <-
  read_table(here::here("data/overlaps/wos_data_simon.txt"), na = c("NULL", "NA", "")) %>% 
  clean_names() %>% 
  remove_empty() %>% 
  filter(str_detect(issn, "^[0-9]{4}-[0-9]{3}[0-9xX]$")) %>% 
  distinct(issn) %>% 
  drop_na(issn)

# total overlap
df %>% 
  mutate(
    issn = str_extract(issn, "[^\n]+")
  ) %>%
  inner_join(df_wos, by = "issn") %>% 
  count()
```

Top 10 countries in overlap:

```{r}
# top 10 countries in overlap
df %>% 
  mutate(
    issn = str_extract(issn, "[^\n]+")
  ) %>%
  inner_join(df_wos, by = "issn") %>% 
  count(country) %>% 
  arrange(-n) %>% 
  head(10) %>% 
  mutate(country = fct_inorder(country) %>% fct_rev()) %>% 
  ggplot(aes(country, n)) +
  geom_col() +
  hrbrthemes::theme_ipsum() +
  coord_flip() +
  labs(
    x = "Country", y = "Number of journals"
  )
```


### Scopus

Total overlap:

```{r}
# Scopus data
df_scopus <-
  read_excel(here::here("data/overlaps/scopus_nov2021.xlsx")) %>%
  clean_names() %>% 
  remove_empty() %>% 
  select(issn = print_issn, e_issn, contains("cite_score"), everything()) %>%
  mutate(issn = if_else(is.na(issn), e_issn, issn)) %>%
  mutate_at(vars(contains("cite_score")), ~ as.numeric(.)) %>% 
  mutate(
    issn = str_replace(issn, "-", "")
  ) %>%
  distinct(issn, .keep_all = T) %>% 
  drop_na(issn)

# total overlap
df %>% 
  drop_na(issn) %>%
  transmute(
    country,
    issn = str_extract(issn, "[^\n]+"),
    issn = str_replace(issn, "-", "")
  ) %>%
  inner_join(df_scopus, by = "issn") %>% 
  count()
```

Top 10 countries in overlap:

```{r}
df %>% 
  drop_na(issn) %>%
  transmute(
    country,
    issn = str_extract(issn, "[^\n]+"),
    issn = str_replace(issn, "-", "")
  ) %>%
  inner_join(df_scopus, by = "issn") %>%
  drop_na(country) %>% 
  count(country) %>% 
  arrange(-n) %>% 
  head(10) %>% 
  mutate(country = fct_inorder(country) %>% fct_rev()) %>% 
  ggplot(aes(country, n)) +
  geom_col() +
  hrbrthemes::theme_ipsum() +
  coord_flip() +
  labs(
    x = "Country", y = "Number of journals"
  )
```


### Dimensions

Total overlap:

```{r}
# Dimensions data
df_dimensions <-
  read_excel(here::here("data/overlaps/journals_dimensions.xlsx")) %>%
  clean_names() %>% 
  remove_empty() %>% 
  select(issn = issn_print, e_issn = issn_e, everything()) %>%
  mutate(issn = if_else(issn == "NULL", e_issn, issn)) %>%
  mutate_at(vars(contains("cite_score")), ~ as.numeric(.)) %>% 
  distinct(issn, .keep_all = T) %>% 
  drop_na(issn)

df %>% 
  drop_na(issn) %>%
  transmute(
    country,
    issn = str_extract(issn, "[^\n]+")
  ) %>%
  inner_join(df_dimensions, by = "issn") %>% 
  count()
```

Top 10 countries in overlap:

```{r}
df %>% 
  drop_na(issn) %>%
  transmute(
    country,
    issn = str_extract(issn, "[^\n]+")
  ) %>%
  inner_join(df_dimensions, by = "issn") %>%
  drop_na(country) %>% 
  count(country) %>% 
  arrange(-n) %>% 
  head(10) %>% 
  mutate(country = fct_inorder(country) %>% fct_rev()) %>% 
  ggplot(aes(country, n)) +
  geom_col() +
  hrbrthemes::theme_ipsum() +
  coord_flip() +
  labs(
    x = "Country", y = "Number of journals"
  )
```

### EBSCO Host

Total Overlap:

```{r}
# EBSCO Host
df_ebsco <-
  read_excel(here::here("data/overlaps/ebscohost.xls")) %>%
  clean_names() %>% 
  remove_empty() %>% 
  distinct(issn) %>% 
  drop_na(issn)

df %>% 
  drop_na(issn) %>%
  transmute(
    country,
    issn = str_extract(issn, "[^\n]+")
  ) %>%
  inner_join(df_ebsco, by = "issn") %>% 
  count()
```

Top 10 countries in overlap:

```{r}
df %>% 
  drop_na(issn) %>%
  transmute(
    country,
    issn = str_extract(issn, "[^\n]+")
  ) %>%
  inner_join(df_ebsco, by = "issn") %>%
  drop_na(country) %>% 
  count(country) %>% 
  arrange(-n) %>% 
  head(10) %>% 
  mutate(country = fct_inorder(country) %>% fct_rev()) %>% 
  ggplot(aes(country, n)) +
  geom_col() +
  hrbrthemes::theme_ipsum() +
  coord_flip() +
  labs(
    x = "Country", y = "Number of journals"
  )
```

### Google Scholar

```{r, eval=F}
# Extract URLs for gscholar script implemented in python

df %>%
  separate(oai_url, c("url1", "url2"), "\n") %>% 
  remove_empty() %>% 
  rename(oai_url = url1) %>% 
  filter(!str_detect(oai_url, "\\?page=")) %>% 
  transmute(
    country, total_record_count, context_name,
    url = str_replace(oai_url, "index/oai", set_spec),
    url = str_replace(url, "^https://", ""),
    url = str_replace(url, "^http://", ""),
    url = str_replace(url, "^www108.", ""),
    url = str_replace(url, "^www5.", ""),
    url = str_replace(url, "^www3.", ""),
    url = str_replace(url, "^www2.", ""),
    url = str_replace(url, "^www.", ""),
  ) %>%
  bind_rows(
    df %>%
      separate(oai_url, c("url1", "url2"), "\n") %>% 
      remove_empty() %>% 
      rename(oai_url = url1) %>% 
      filter(str_detect(oai_url, "\\?page=")) %>% 
      transmute(
        country, total_record_count, context_name,
        url = str_replace(oai_url, "oai$", set_spec),
        url = str_replace(url, "^https://", ""),
        url = str_replace(url, "^http://", ""),
        url = str_replace(url, "^www108.", ""),
        url = str_replace(url, "^www5.", ""),
        url = str_replace(url, "^www3.", ""),
        url = str_replace(url, "^www2.", ""),
        url = str_replace(url, "^www.", ""),
      ), .
  ) %>% 
  write_csv(here::here("data/gscholar_urls.csv"))
```


Total overlap:

```{r, fig.retina=4}
# Read in python processed google scholar URLs

df_gscholar <- 
  read_csv(here::here("scripts/gscholar_urls_mapped.csv")) %>% 
  select(-result_json) %>% 
  mutate(n_results = parse_integer(n_results))

df_gscholar <-
  df %>%
  separate(oai_url, c("url1", "url2"), "\n") %>% 
  remove_empty() %>% 
  rename(oai_url = url1) %>% 
  filter(!str_detect(oai_url, "\\?page=")) %>% 
  transmute(
    country, total_record_count, context_name,
    url = str_replace(oai_url, "index/oai", set_spec),
    url = str_replace(url, "^https://", ""),
    url = str_replace(url, "^http://", ""),
    url = str_replace(url, "^www108.", ""),
    url = str_replace(url, "^www5.", ""),
    url = str_replace(url, "^www3.", ""),
    url = str_replace(url, "^www2.", ""),
    url = str_replace(url, "^www.", ""),
  ) %>%
  bind_rows(
    df %>%
      separate(oai_url, c("url1", "url2"), "\n") %>% 
      remove_empty() %>% 
      rename(oai_url = url1) %>% 
      filter(str_detect(oai_url, "\\?page=")) %>% 
      transmute(
        country, total_record_count, context_name,
        url = str_replace(oai_url, "oai$", set_spec),
        url = str_replace(url, "^https://", ""),
        url = str_replace(url, "^http://", ""),
        url = str_replace(url, "^www108.", ""),
        url = str_replace(url, "^www5.", ""),
        url = str_replace(url, "^www3.", ""),
        url = str_replace(url, "^www2.", ""),
        url = str_replace(url, "^www.", ""),
      ), .
  ) %>% 
  distinct() %>% 
  inner_join(df_gscholar, by = "url")

# total overlap
df_gscholar %>% 
  mutate(present = n_results > 0) %>%
  filter(present) %>% 
  count()
```

Top 10 countries in overlap:

```{r}
# top 10 countries in overlap
df_gscholar %>% 
  mutate(present = n_results > 0) %>%
  filter(present) %>% 
  count(country) %>% 
  arrange(-n) %>% 
  mutate(country = fct_inorder(country) %>% fct_rev()) %>% 
  head(10) %>% 
  ggplot(aes(country, n)) +
  geom_col() +
  scale_y_continuous(breaks = scales::breaks_width(1000)) +
  theme_minimal() +
  coord_flip() +
  labs(x = "Country", y = "Total journals")
```


Number of articles:

```{r, fig.retina=4}
# number of articles
df_gscholar %>%
  left_join(read_csv(here::here("scripts/gscholar_citations.csv")), by = "url") %>%
  mutate(n_results = pmin(n_results, 500)) %>% 
  ggplot(aes(n_results)) +
  geom_histogram(binwidth = 10, color = "black", alpha = 0.75) +
  scale_x_continuous(labels = c("0", "100", "200", "300", "400", "500+")) +
  hrbrthemes::theme_ipsum() +
  labs(
    x = "Number of articles",
    y = "Number of journals"
  )
```


Number of citations on first Scholar page:

```{r}
# number of citations on first gscholar page
df_gscholar %>%
  left_join(read_csv(here::here("scripts/gscholar_citations.csv")), by = "url") %>%
  mutate(n_citations = pmin(n_citations, 500)) %>% 
  ggplot(aes(n_citations)) +
  geom_histogram(binwidth = 10, color = "black", alpha = 0.75) +
  scale_x_continuous(labels = c("0", "100", "200", "300", "400", "500+")) +
  hrbrthemes::theme_ipsum() +
  labs(
    x = "Number of citations on first page",
    y = "Number of journals"
  )
```


